---
title: "Affective Math Multi linear Regression Mixed Effects"
author: "Fettah Kiran"
subtitle: "FP, HR E4, HR AW, HRV | N = 50"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    theme: united
    number_sections: true 
    mathjax: default
  pdf_document: 
    toc: true
    number_sections: true 
    keep_tex: true
header-includes:
  - \usepackage[table]{xcolor}
  - \definecolor{myGray}{gray}{0.8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

------------------------------------------------------------------------

*Notes:* 

- Qlevel data is created by grouping the raw trial‑level data by participant, question type, and question name, and then computing the mean outcome within each group.
- All inferential analyses were carried out with linear mixed‑effects models that include a participant‑centered random intercept to account for between‑subject variability.

`Reference for Question Type: "V"`

------------------------------------------------------------------------

```{r include=FALSE}
rm(list = ls())
dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(dir)
getwd()
```

\newpage

```{r include=FALSE}
# library(tidyverse)
# library(lubridate)
# library(ggplot2)
# library(cowplot)
# library(ggpubr)
# library(readr)
# library(gridExtra)
# library(dplyr)
# library(tidyr)
# library(knitr)
# library("car")
# library(lme4)
# library(lmerTest)
# library(lattice)
# library(sjPlot)
# library(Matrix)
# require(ggpmisc) # for stat_poly_eq
# library(reshape2)
# library(kableExtra)
# library(psych) ## Collinearity Plot
# library(jtools)
# library(latex2exp) # parses and converts LaTeX math formulas to R's plotmath expressions
# library(ggeffects)
# library(scales) ## scales::label_number()

source("requirements.R")

```


```{r SpecialThemes, message=FALSE, warning=FALSE}


# Load custom functions
#browseURL("fm_plot_func.R")
source("fm_plot_func.R")

# options(digits=3)
theme_set(theme_classic()) # set the theme to classic
theme_update(plot.title = element_text(hjust = 0.5)) # center the title

my_theme_bold.italic <- my_theme + theme(text = element_text(size = 14, face = "bold"))

data_dir = "../data/processed/" # data directory
plot_dir = "../figures/" # plot directory

is_save <- TRUE
```

\newpage
# Read Qeustion Level Data
```{r readRawData, include=FALSE}
N <- 50

file = sprintf("%sTAFFC_Qlevel_Data_N%s.csv", data_dir, N)

Qlevel = read.csv(file, header = TRUE, sep = ",", stringsAsFactors = T)


names(Qlevel)

Qlevel$Question.Type <- factor(Qlevel$Question.Type, levels = c("V", "A", "W"))
Qlevel$Gender <- relevel(factor(Qlevel$Gender), ref = "M")
Qlevel$Grade <- relevel(factor(Qlevel$Grade), ref = "0")

PP.len <- colSums(!is.na(Qlevel))[["PPNorm"]]
HRE4.len <- colSums(!is.na(Qlevel))[["HR.E4Norm"]]
HRAW.len <- colSums(!is.na(Qlevel))[["HR.AWNorm"]]
HRV.len <- colSums(!is.na(Qlevel))[["HRVNorm"]]


# All variables are scaled. 
PP_unit <- "scaled"
HR_unit = "scaled" 
HRV_unit = "scaled"

# build the full y‐label string
pp_y_lab <- sprintf("$\\bar{ \\textit{NFP}}$ \\[%s\\]", PP_unit)
hre4_y_lab = sprintf("$\\bar{ \\textit{NHR}}_{E4 }$ [%s]", HR_unit)
hraw_y_lab = sprintf("$\\bar{ \\textit{NHR}}_{AW }$ [%s]", HR_unit)
hrv_y_lab = sprintf("$\\bar{ \\textit{NHRV}}$ [%s]", HRV_unit)



```


## Collinearity Check for all predictors

```{r Multi-Regr-Collinearity-Plot, fig.height=6, fig.width=7, message=FALSE, warning=FALSE}
library(ggcorrplot)
library(ggtext)
library(psych)

reduced_data <- subset(Qlevel, select = c(SAI, QTime, Question.Type, Gender, Grade))

reduced_data <- reduced_data %>%
  # rename your time variable
  rename(QTIME = QTime,
         QTYPE = Question.Type,
         SEX = Gender
         )

corr_matrix <- model.matrix(~., data=reduced_data)
correlation_plot <- cor((corr_matrix), use="everything") 

colnames(correlation_plot) = rownames(correlation_plot) <- c("Intercept","*SAI*", "*QTIME*","*QTYPE* &nbsp; [*A*]", "*QTYPE* &nbsp; [*W*]",  "*SEX* &nbsp; [*F*]","*QGRADE* &nbsp; [1]" )

corr.plot <- (ggcorrplot(correlation_plot, show.diag=FALSE, type="lower", lab=TRUE) + 
                theme(axis.text = element_markdown()))

corr.plot


library(data.table) 
  
set.seed(1) 
  
# counting frequencies of factor 
# levels 
setDT(reduced_data)[, .N, keyby=QTYPE] 

detach("package:psych", unload=TRUE)

if (is_save == TRUE) {
  plot_path <- sprintf("%sFigure8.pdf", plot_dir) # Collinearity_Plot.pdf
  ggsave(plot_path, corr.plot, width = 7, height = 6)
}



```

\newpage

# Model 1 - PPNorm with best correction

```{r M1_full, echo=FALSE, message=FALSE, warning=FALSE}

M1.pp.fit.fm <- lmer(scale(PPNorm) ~ (1 | ParticipantID) + scale(SAI) + Question.Type + scale(QTime) + Grade + Gender, data = Qlevel, REML = FALSE)

# Summary statistics of the full model
summary(M1.pp.fit.fm)
summ(M1.pp.fit.fm, digits = 3)
```

\newpage

## Backward-Direction Elimination (BDE)

```{r echo=FALSE}
step_bd <- step(M1.pp.fit.fm, direction = "backward")
step_bd # Display elimination results

FM = get_model(step_bd) # Display the final model
```

\newpage

## PP Final Model

```{r echo=FALSE, message=FALSE, warning=FALSE}
M1.pp.fit.FM <- lmer(scale(PPNorm) ~ (1 | ParticipantID) + Question.Type + Gender, data = Qlevel, REML = FALSE)

summary(M1.pp.fit.FM, digits = 3)
summ(M1.pp.fit.FM, digits = 3)

```

\newpage

## Plot Final Model

```{r fig.height=5, fig.width=6}

ylims <- c(-0.7, 0.5)

# Question Type Final Model
pp.qt.pm.fm <- ggpredict(M1.pp.fit.FM,
  terms = c("Question.Type")
) %>%
  mutate(group = as.factor(c("1", "2", "3"))) %>%
  drop_na() %>% 
  gather(key = "key", value = "value", conf.low, conf.high) %>%
  ggplot() +
  geom_line(aes(x = x, y = value, color = group), size = 2) +
  geom_point(aes(x = x, y = predicted, color = group, size = 2)) +
  scale_y_continuous(
      limits = c(-0.7, 0.5),
      breaks = seq(-0.7, 0.5, by = 0.3),
      labels = scales::label_number(accuracy = 0.1)   # <— no scientific notation
    ) +
  scale_color_manual(values = c("gray", "cyan", "red")) +
  my_theme_pred +
  labs(x = "", y = TeX(pp_y_lab))


# pp.qt.pm.fm # will be used to compare 3 models

pp.gender.pm.fm <- ggpredict(M1.pp.fit.FM,
  terms = c("Gender")
) %>%
  mutate(group = as.factor(c("1", "2"))) %>%
  drop_na() %>% # check # of levels you've
  gather(key = "key", value = "value", conf.low, conf.high) %>%
  ggplot() +
  geom_line(aes(x = x, y = value, color = group), size = 2) +
  geom_point(aes(x = x, y = predicted, color = group, size = 2)) +
  scale_y_continuous(limits = ylims, guide = "none") + # "none" removes the y-axis ticks and labels
  scale_color_manual(values = c("gray", "cyan")) +
  my_theme_pred + 
  
  labs(x = "", y = "")

# pp.gender.pm.fm 


final.w.legend <- cowplot::plot_grid(pp.qt.pm.fm, mylegend, pp.gender.pm.fm ,
  nrow = 3,
  rel_heights = c(1, 0.1, 1),
  labels = c("a", "", "b")
)

final.w.legend
```



### Fixed Effects Visualization of PP Model

```{r fig.height=4.5, fig.width=7, message=FALSE, warning=FALSE}
## - Why Gender 2 star, while one star in the final model?

pp.fm.plot.pred <- sjPlot::plot_model(M1.pp.fit.FM,
  show.values = TRUE, show.p = TRUE,
  value.offset = 0.1,
  title = ""
) #+ my_theme1

pp.fm.plot.pred$layers[[3]]$aes_params$vjust <- (0.1)
pp.fm.plot.pred$layers[[3]]$aes_params$hjust <- (-0.1)


pp.fm.plot.pred

# # random effect
# plot_model(M1.pp.fit.FM, "re")
```

### Diagnostic on Model residuals

```{r M1_Diagnostic, echo=FALSE}
M1.pp.fit.FM.res <- residuals(M1.pp.fit.FM, type = "pearson")

qqnorm(M1.pp.fit.FM.res, main = "Normal Q-Q Plot | M1 residuals")
qqline(M1.pp.fit.FM.res, col = "red")
```

\newpage

# Model 2 - HR E4 Full Model

```{r M2_fm, echo=FALSE, message=FALSE, warning=FALSE}
M2.fit.fm <- lmer(scale(HR.E4Norm) ~ (1 | ParticipantID) + scale(SAI) + Question.Type + scale(QTime) + Grade + Gender, data = Qlevel, REML = FALSE)

# Summary statistics of the full model
summary(M2.fit.fm)
summ(M2.fit.fm, digits = 3)
```

\newpage

## Backward-Direction Elimination (BDE)

```{r echo=FALSE}
step_bd <- step(M2.fit.fm, direction = "backward")
step_bd # Display elimination results

FM = get_model(step_bd) # Display the final model
```

\newpage

## HR E4 Final Model

```{r M2_FM, echo=FALSE, message=FALSE, warning=FALSE}
M2.fit.FM <- lmer(scale(HR.E4Norm) ~ (1 | ParticipantID) + Question.Type, data = Qlevel, REML = FALSE)

#M2.fit.FM <- lmer(FM, data = Qlevel, REML = FALSE)

summary(M2.fit.FM, digits = 3)
summ(M2.fit.FM, digits = 3)
```

\newpage

## Plot Final Model

```{r message=FALSE, warning=FALSE}

hre4.qt.pm.fm <- ggpredict(M2.fit.FM, terms = c("Question.Type")) %>%
  mutate(group = as.factor(c("1", "2", "3"))) %>%
  drop_na() %>% # check # of levels you've
  gather(key = "key", value = "value", conf.low, conf.high) %>%
  ggplot() +
  geom_line(aes(x = x, y = value, color = group), size = 2) +
  geom_point(aes(x = x, y = predicted, color = group, size = 2)) +
  scale_y_continuous(
      limits = c(-0.7, 0.5),
      breaks = seq(-0.7, 0.5, by = 0.3),
      labels = scales::label_number(accuracy = 0.1)   # <— no scientific notation
    ) +
  scale_color_manual(values = c("gray", "red", "red")) +
  my_theme_pred +
  labs(x = "", 
       y = TeX(hre4_y_lab)
       )
  

hre4.qt.pm.fm
```

### Fixed Effects Visualization of HR E4 Model

```{r fig.height=4.5, fig.width=7}

pp.fm.plot.pred <- sjPlot::plot_model(M2.fit.FM,
  show.values = TRUE, show.p = TRUE,
  title = expression(bold(paste(bar(Delta * " " * bolditalic(HR[E4]) * ""), " Final Model ")))
) + my_theme1

pp.fm.plot.pred$layers[[3]]$aes_params$vjust <- (0.1)
pp.fm.plot.pred$layers[[3]]$aes_params$hjust <- (0.3)

pp.fm.plot.pred
```

## Diagnostic on Model residuals

```{r echo=FALSE}
M2.fit.FM.res <- residuals(M2.fit.FM, type = "pearson")

qqnorm(M2.fit.FM.res, main = "Normal Q-Q Plot | HR E4 residuals")
qqline(M2.fit.FM.res, col = "red")
```


\newpage

# Model 3 - HR AW Full Model

```{r echo=FALSE, message=FALSE, warning=FALSE}
M3.fit.fm <- lmer(scale(HR.AWNorm) ~ (1 | ParticipantID) + scale(SAI) + Question.Type + scale(QTime) + Grade + Gender, data = Qlevel, REML = FALSE)

# Summary statistics of the full model
summary(M3.fit.fm, digits = 3)
summ(M3.fit.fm, digits = 3)
```


\newpage

## Backward-Direction Elimination (BDE)

```{r echo=FALSE}
step_bd <- step(M3.fit.fm, direction = "backward")
step_bd # Display elimination results

FM = get_model(step_bd) 
```

\newpage

## HR AW Final Model

```{r echo=FALSE, message=FALSE, warning=FALSE}
M3.fit.FM <- lmer(scale(HR.AWNorm) ~ (1 | ParticipantID) + Question.Type + scale(QTime) + Grade, data = Qlevel, REML = FALSE)

summary(M3.fit.FM, digits = 3)
summ(M3.fit.FM, digits = 3)

```

\newpage

## Plot Final Model

```{r message=FALSE, warning=FALSE}
# Question Type Final Model
hr_aw.qt.pm.fm <- ggpredict(M3.fit.FM, terms = c("Question.Type")) %>%
  mutate(group = as.factor(c("1", "2", "3"))) %>%
  drop_na() %>% # check # of levels you've

  gather(key = "key", value = "value", conf.low, conf.high) %>%
  ggplot() +
  geom_line(aes(x = x, y = value, color = group), size = 2) +
  geom_point(aes(x = x, y = predicted, color = group, size = 2)) +
  scale_color_manual(values = c("gray", "red", "red")) +
  #scale_y_continuous(limits = ylims) + # "none" removes the y-axis ticks and labels
  scale_y_continuous(
      limits = c(-0.7, 0.5),
      breaks = seq(-0.7, 0.5, by = 0.3),
      labels = scales::label_number(accuracy = 0.1)   # <— no scientific notation
    ) +
  my_theme_pred +
  labs(x = "", 
       y = TeX(hraw_y_lab)
       )

# Correctness
hr_aw_grade.pm.fm <- ggpredict(M3.fit.FM, "Grade") %>%
  mutate(group = as.factor(c("1", "2"))) %>%
  drop_na() %>% # check # of levels you've

  gather(key = "key", value = "value", conf.low, conf.high) %>%
  ggplot() +
  geom_line(aes(x = x, y = value, color = group), size = 2) +
  geom_point(aes(x = x, y = predicted, color = group, size = 2)) +
  theme_bw() +
  scale_color_manual(values = c("gray", "orange")) +
  scale_y_continuous(limits = ylims, guide = "none") + # "none" removes the y-axis ticks and labels
  my_theme_pred_quant+ 
  labs(x = "", y = "")

# hr_aw_grade.pm.fm

# Solving Time
hr_aw_st.pm.fm <- ggpredict(M3.fit.FM, "QTime") %>%
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2) +
  geom_line(colour = "cyan", size = 2) +
  geom_vline(
    xintercept = mean(Qlevel$QTime),
    linetype = "dashed",
    color = "black",
    size = 1
  ) +
  scale_y_continuous(limits = ylims, guide = "none") + # "none" removes the y-axis ticks and labels
  my_theme_pred_quant + 
  labs(x = "", y = "")

# hr_aw_st.pm.fm

cowplot::plot_grid(
  hr_aw.qt.pm.fm, hr_aw_grade.pm.fm, hr_aw_st.pm.fm, 
  ncol = 3,
  scale = c(.97, .97, .97),
  labels = c("a", "b", "c"),
  label_size = 20
)

```

### Fixed Effects Visualization of HR AW Model

```{r fig.height=4.5, fig.width=7}

pp.fm.plot.pred <- sjPlot::plot_model(M3.fit.FM,
  show.values = TRUE, show.p = TRUE,
  title = expression(bold(paste(bar(Delta * " " * bolditalic(HR))[AW] * "", " Final Model ")))
) + my_theme1

pp.fm.plot.pred$layers[[3]]$aes_params$vjust <- (0.1)
pp.fm.plot.pred$layers[[3]]$aes_params$hjust <- (0.3)

pp.fm.plot.pred
```

## Diagnostic on Model residuals

```{r echo=FALSE}
# Diagnostic on Model residuals

M3.fit.FM.res <- residuals(M3.fit.FM, type = "pearson")

qqnorm(M3.fit.FM.res, main = "HR AW Final Moldel residuals")
qqline(M3.fit.FM.res, col = "red")
```



\newpage

# Model 4 - NHRV Full Model

```{r echo=FALSE, message=FALSE, warning=FALSE}
## NRHV model
M4.fit.fm <- lmer(scale(HRVNorm) ~ (1 | ParticipantID) + scale(SAI) + Question.Type + scale(QTime) + Grade + Gender, data = Qlevel, REML = FALSE)

# Summary statistics of the full model
summary(M4.fit.fm)
summ(M4.fit.fm, digits = 3)
```



\newpage

## Backward-Direction Elimination (BDE)

```{r echo=FALSE}
step_bd <- step(M4.fit.fm, direction = "backward")
step_bd # Display elimination results
FM = get_model(step_bd) # Display the final model
```

\newpage

## HRV Final Model

```{r echo=FALSE, message=FALSE, warning=FALSE}
M4.fit.FM <- lmer(scale(HRVNorm) ~ (1 | ParticipantID) + Question.Type + Grade, data = Qlevel, REML = FALSE)

summary(M4.fit.FM, digits = 3)
summ(M4.fit.FM, digits = 3)
```

\newpage

## Plot Final Model

```{r fig.height=5, fig.width=6}
# Question Type Final Model
hrv.qt.pm.fm <- ggpredict(M4.fit.FM,
  terms = c("Question.Type")
) %>%
  mutate(group = as.factor(c("1", "2", "3"))) %>%
  drop_na() %>% # check # of levels you've
  gather(key = "key", value = "value", conf.low, conf.high) %>%
  ggplot() +
  geom_line(aes(x = x, y = value, color = group), size = 2) +
  geom_point(aes(x = x, y = predicted, color = group, size = 2)) +
  scale_color_manual(values = c("gray", "red", "red")) +
  my_theme_pred +
  scale_y_continuous(
      limits = c(-0.7, 0.5),
      breaks = seq(-0.7, 0.5, by = 0.3),
      labels = scales::label_number(accuracy = 0.1)   # <— no scientific notation
    ) +
  labs(x = "", 
       y = TeX(hrv_y_lab)
       )


# hrv.qt.pm.fm



# Correctness
hrv_grade.pm.fm <- ggpredict(M4.fit.FM, "Grade") %>%
  mutate(group = as.factor(c("1", "2"))) %>%
  drop_na() %>% # check # of levels you've
  gather(key = "key", value = "value", conf.low, conf.high) %>%
  ggplot() +
  geom_line(aes(x = x, y = value, color = group), size = 2) +
  geom_point(aes(x = x, y = predicted, color = group, size = 2)) +
  theme_bw() +
  scale_color_manual(values = c("gray", "cyan")) +
  scale_y_continuous(limits = ylims, guide = "none") + # "none" removes the y-axis ticks and
  my_theme_pred_quant +
  labs(x = "", 
       y = ""
       )


final.w.legend <- cowplot::plot_grid(hrv.qt.pm.fm, hrv_grade.pm.fm, mylegend,
  nrow = 2,
  rel_heights = c(1,0.1)
)

final.w.legend
```

### Fixed Effects Visualization of HRV Model

```{r fig.height=4.5, fig.width=7, message=FALSE, warning=FALSE}

pp.fm.plot.pred <- sjPlot::plot_model(M4.fit.FM,
  show.values = TRUE, show.p = TRUE,
  title = expression(bold(paste(bar(" " * bolditalic(HRV) * ""), " Final Model ")))
) + my_theme1 #+ xlim(-0.2, 0.2)

pp.fm.plot.pred$layers[[3]]$aes_params$vjust <- (1.1)
pp.fm.plot.pred$layers[[3]]$aes_params$hjust <- (0.7)

#pp.fm.plot.pred$data$term <- c("Question.TypeA", "Question.TypeW", "Grade")

pp.fm.plot.pred

```

## Diagnostic on Model residuals

```{r echo=FALSE}
M4.fit.FM.res <- residuals(M4.fit.FM, type = "pearson")

qqnorm(M4.fit.FM.res, main = "Normal Q-Q Plot | M4 residuals")
qqline(M4.fit.FM.res, col = "red")
```


\newpage

# Paper figures 

## 1-Multi-Regression-Plots.pdf

```{r echo=FALSE, fig.height=11, fig.width=8}
# QType, Gender, Grade, QTime

pp.qt.pm.fm <- pp.qt.pm.fm + ggtitle(TeX("\\textit{QTYPE}"))
pp.gender.pm.fm <- pp.gender.pm.fm + ggtitle(TeX("\\textit{SEX}"))



#PP row
row1 <- cowplot::plot_grid(
  pp.qt.pm.fm, pp.gender.pm.fm , 
  nrow = 1,
  scale = c(.97, .97),
  labels = c("a1", "" ),
  label_size = 20
)

#HR AW row
hr_aw.qt.pm.fm <- hr_aw.qt.pm.fm + ggtitle("")
hr_aw_grade.pm.fm <- hr_aw_grade.pm.fm + ggtitle( TeX("\\textit{QGRADE}"))
row2 <- cowplot::plot_grid(
  hr_aw.qt.pm.fm, hr_aw_grade.pm.fm, #hr_aw_st.pm.fm,
  nrow = 1,
  scale = c(.97, .97),
  labels = c("a2", ""),
  label_size = 20
)


#HR E4 row
hre4.qt.pm.fm <- hre4.qt.pm.fm + ggtitle("")

row3 <- cowplot::plot_grid(
  hre4.qt.pm.fm, NULL, 
  nrow = 1,
  scale = c(.97, .97),
  labels = c("a3", ""),
  label_size = 20
)

# HRV row
hrv.qt.pm.fm <- hrv.qt.pm.fm + ggtitle("")
hrv_grade.pm.fm <- hrv_grade.pm.fm +  ggtitle( TeX("\\textit{QGRADE}"))
row4 <- cowplot::plot_grid(
hrv.qt.pm.fm,  hrv_grade.pm.fm,
  nrow = 1,
  scale = c(.97, .97),
  labels = c("a4", ""),
  label_size = 20
)


# --- 2. assume you already have this from before: ---
final_5M <- cowplot::plot_grid(
  row1, row2, row3, row4, mylegend,
  nrow = 5,
  rel_heights = c(1, 1, 1, 1, 0.1)
)

final_5M


# # --- 1. build the title row ---
# title_row <- ggdraw() +
#   # Four labels centered at 1/8, 3/8, 5/8, 7/8 of the width
#   draw_label("QTYPE", x = 1/8, y = 0.5, fontface = "bold", hjust = 0.5) +
#   draw_label("SEX",           x = 3/8, y = 0.5, fontface = "bold", hjust = 0.5) +
#   draw_label("GRADE",         x = 5/8, y = 0.5, fontface = "bold", hjust = 0.5) +
#   draw_label("QTIME [s]", x = 7/8, y = 0.5, fontface = "bold", hjust = 0.5) +
#   theme(plot.margin = margin(0, 0, 0, 0))



# # --- 3. stack the title row on top ---
# final_with_headers <- cowplot::plot_grid(
#   title_row,
#   final_5M,
#   ncol  = 1,
#   rel_heights = c(0.05, 0.95)   # ~5% height for headers, 95% for your grid
# )

# --- 4. draw it ---
#print(final_with_headers)



```

```{r echo=FALSE, fig.height=11, fig.width=8}

final_5M
# #Save the final_5M plot
ggsave(
  #filename = sprintf("%s1-Multi-Regression-Plots.pdf", plot_dir),
  filename = sprintf("%sFigure11.pdf", plot_dir),
  plot = final_5M,
  width = 8,
  height = 11,
  dpi = 300
)
```


# Table

```{r}
summ(M1.pp.fit.FM, digits = 3)$model@call
M1_table = summ(M1.pp.fit.FM, digits = 3)$coeftable

summ(M2.fit.FM, digits = 3)$model@call
M2_table = summ(M2.fit.FM, digits = 3)$coeftable

summ(M3.fit.FM, digits = 3)$model@call
M3_table = summ(M3.fit.FM, digits = 3)$coeftable


summ(M4.fit.FM, digits = 3)$model@call
M4_table = summ(M4.fit.FM, digits = 3)$coeftable


merge <- rbind(M1_table, M2_table, M3_table, M4_table)


```



```{r model-table, include=FALSE, results='asis'}
library(dplyr)
library(purrr)
library(knitr)

# 1) Put your models in a named list
models <- list(
  fEDA  = M1.pp.fit.FM,
  HR_AW = M3.fit.FM,
  HR_E4 = M2.fit.FM,
  HRV   = M4.fit.FM
)

# 2) extract each summary(...$coefficients) into a data.frame
coef_dfs <- lapply(models, function(mod) {
  co <- summ(mod, digits = 3)$coeftable
  #as.data.frame(co, stringsAsFactors = FALSE)
  as.data.frame(co, stringsAsFactors = FALSE) %>% dplyr::select(-4)
})

# assume coef_dfs is your list of 4 data.frames,
# each with rownames = predictor names and columns Est., S.E., t val., d.f., p

# 1) figure out every predictor that appears in any model
all_preds <- unique(unlist(lapply(coef_dfs, rownames)))

# 2) for each df, turn rownames into a column, 
#    re-order to 'all_preds', and then put rownames back
aligned <- lapply(coef_dfs, function(df) {
  df2 <- as.data.frame(df, stringsAsFactors=FALSE)
  df2$Predictor <- rownames(df2)
  
  # reorder (and insert NA rows for missing preds)
  df2 <- df2[match(all_preds, df2$Predictor), , drop=FALSE]
  
  # restore rownames
  rownames(df2) <- all_preds
  df2
})

# 3) drop the extra Predictor columns except in the first
for(i in seq_along(aligned)) {
  aligned[[i]]$Predictor <- NULL
}


# 4) now cbind them
merged <- do.call(cbind, aligned)

# 5) restore a single Predictor column in front
merged <- cbind(Predictor = rownames(merged), merged, row.names=NULL)


# Select all columns that end with ".Est." and drop them
Est_all <- merged %>% dplyr::select(Predictor,ends_with(".Est."))
SE_all <- merged %>% dplyr::select(Predictor,ends_with(".S.E."))
t_all <- merged %>% dplyr::select(Predictor,ends_with(".t val."))
p_all <- merged %>% dplyr::select(Predictor,ends_with(".p"))

paper_merged <- cbind(Est_all, SE_all[, -1], t_all[, -1], p_all[, -1])

```



```{r merged-table, results='asis', echo=FALSE}

# 2) Build your header labels
stat_labels  <- c("Est", "S.E.", "t", "p")
# bottom row: model names repeated under each stat
model_names  <- c("fEDA", "HRAW", "HRE4", "HRV")
var_labels   <- rep(model_names, times = length(stat_labels))

# define a very light and a medium light gray
light_gray  <- if (knitr::is_latex_output()) "gray!25" else "#E6E6E6"
medium_gray <- if (knitr::is_latex_output()) "gray!50" else "#CCCCCC"


paper_merged %>%  
  mutate(
    across(
      ends_with(".p"),
      ~ round(., 3)
    )
  ) %>%
  mutate(
    across(
      ends_with(".p"),
      ~ format.pval(., digits = 3, eps = 0.001)
    )
  ) %>%  mutate(
    across(
      ends_with(".t val"),
      ~ round(., 3)
    )
  ) %>% 
  kable(
  digits = 3,
  format          = "html",
  #format          = "latex",
  booktabs        = TRUE,
  escape          = TRUE,
  table.placement = "H",
  col.names       = c("Predictor", var_labels),
  align           = c("l", rep("r", length(var_labels)))
) %>%
  add_header_above(
    header = c(
      " "    = 1,
      "Coefficient $b.$"    = 4,
      "$S.E.$" = 4,
      "$t$ value" = 4,
      "Pr(>$|z|$)"  = 4
    ),
    bold = TRUE
  ) %>%
  column_spec(c(3,7, 11,15),   background = light_gray) %>% # myGray (0.8), #"gray!15"
  column_spec(c(5, 9, 13 ,17),   background = medium_gray) %>%  # gray 0.7
  column_spec(c(4,6,8),   background = "white")    %>%
  kable_styling(
    latex_options = c("hold_position","scale_down"),
    font_size     = 11
  )
```


