---
title: "Affective-Math Stress Models - N = 50"
author: "Fettah Kiran"
subtitle: "Stress.FP, Stress.HRE4, Stress.HRAW, Stress.HRV | N = 50"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    theme: united
    number_sections: true 
  #latex_engine: pdflatex
  pdf_document: 
    toc: true
    number_sections: true 
    keep_tex: true
    extra_dependencies:
      - float
      - booktabs
      - caption
      - multirow
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

```{r include=FALSE}
rm(list = ls())
dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(dir)
getwd()
```

\newpage


MODEL: \
Model1: Stress FP \
Model2: Stress HR.AW \
Model3: Stress HR.E4 \
Model4: Stress HRV \



```{r include=FALSE}
# library(tidyverse)
# library(lubridate)
# library(ggplot2)
# library(cowplot)
# library(ggpubr)
# library(readr)
# library(gridExtra)
# library(dplyr)
# library(tidyr)
# library(knitr)
# library("car")
# library(lme4)
# library(lmerTest)
# library(lattice)
# library(sjPlot)
# library(Matrix)
# require(ggpmisc) # for stat_poly_eq
# library(reshape2)
# library(kableExtra)
# library(bestNormalize)
# library(jtools) # summ function
# library(latex2exp) # parses and converts LaTeX math formulas to R's plotmath expressions

source("requirements.R")
```



```{r SpecialThemes, message=FALSE, warning=FALSE}
theme_set(theme_classic()) # set the theme to classic
theme_update(plot.title = element_text(hjust = 0.5)) # center the title

# Load custom functions
#browseURL("fm_plot_func.R")
source("fm_plot_func.R")

data_dir = "../data/processed/" # data directory
plot_dir = "../figures/" # plot directory

is_save <- FALSE
```

\newpage


# Read TAFFC_Qlevel_Data_N50.csv

```{r readRawData, include=FALSE}
N <- 50


file = sprintf("%sTAFFC_Qlevel_Data_N%s.csv", data_dir, N)

Qlevel = read.csv(file, header = TRUE, sep = ",", stringsAsFactors = T)


names(Qlevel)

Qlevel$Question.Type <- factor(Qlevel$Question.Type, levels = c("V", "A", "W"))
Qlevel$Gender <- relevel(factor(Qlevel$Gender), ref = "M")
Qlevel$Grade <- relevel(factor(Qlevel$Grade), ref = "0")

```

# QLevel Data 

```{r Qlevel_Simple}


Qlevel$Gender <- as.character(Qlevel$Gender)
# Relevel the factors
#Qlevel$Gender < factor(Qlevel$Gender, levels = c("F", "M"))
Qlevel$Gender <- relevel(factor(Qlevel$Gender), ref = "M")
Qlevel$Grade <- relevel(factor(Qlevel$Grade), ref = "0")
levels(Qlevel$Gender)
levels(Qlevel$Grade)
# [1] "M" "F"

Qlevel$Question.Type <- factor(Qlevel$Question.Type, levels = c("V", "A", "W"))

```



### Simple Stress Labeling: PP, HR.E4, HR.AW,  HRVNorm 


```{r Test, include=FALSE}
library(dplyr)

# 2) Join stats back, label stress, drop any missing physiology, and set factor levels
Qlevel_Simpl_Stress <- Qlevel %>%
  mutate(
    Stress.pp   = factor(if_else(PPNorm    > PPNorm_mean,    "S", "NS"), levels = c("NS","S")),
    Stress.hre4 = factor(if_else(HR.E4Norm  > HR.E4Norm_mean,  "S", "NS"), levels = c("NS","S")),
    Stress.hraw = factor(if_else(HR.AWNorm  > HR.AWNorm_mean,  "S", "NS"), levels = c("NS","S")),
    Stress.nhrv = factor(if_else(HRVNorm    < HRVNorm_mean,    "S", "NS"), levels = c("NS","S")),

    Gender      = factor(Gender, levels = c("F","M")),
    QType       = factor(QType,  levels = c("V","A","W"))
  )

# 3) (Optional) Inspect how many, if any, rows were dropped due to missing physiology
n_before <- nrow(Qlevel)
n_after  <- nrow(Qlevel_Simpl_Stress)
cat(glue::glue("Dropped {n_before - n_after} rows with missing physiology."))

# Done: Qlevel_Simpl_Stress now has all your means, sds, medians, n, 
#      plus four clean Stress.* factors and properly‐leveled Gender/QType.

colSums(!is.na(Qlevel_Simpl_Stress))

```



## Qlevel QQ plots for all participants

```{r echo=FALSE, fig.height=3, fig.width=8}
# Plot for PPNorm
PP_stress_qq_all <- ggqqplot(Qlevel_Simpl_Stress$PPNorm,
  ylab = "", xlab = "",
  main = TeX(r'($\bar{\textit{NFP}}$)'),
  ggtheme = my_theme1
)

n_PPNorm <- sum(!is.na(Qlevel_Simpl_Stress$PPNorm))
PP_stress_qq_all <- PP_stress_qq_all + annotate("text", x = 0, y = Inf, hjust = 0.5, vjust = 1.5,  parse = TRUE, size = 5,
                   label = paste0("~italic(n)", " == ", n_PPNorm)
                   )
  

# Plot for HR.AW
HR_AW_stress_qq_all <- ggqqplot(Qlevel_Simpl_Stress$HR.AWNorm,
  ylab = "", xlab = "",
  main = TeX(r'($\bar{\textit{NHR}}_{AW}$)'),
  ggtheme = my_theme1
)

n_HRAWNorm <- sum(!is.na(Qlevel_Simpl_Stress$HR.AWNorm))
HR_AW_stress_qq_all <- HR_AW_stress_qq_all + annotate("text", x = 0, y = Inf, hjust = 0.5, vjust = 1.5,  parse = TRUE, size = 5,
                   label = paste0("~italic(n)", " == ", n_HRAWNorm)
                   )


# Plot for HR.E4
HR_E4_stress_qq_all <- ggqqplot(Qlevel_Simpl_Stress$HR.E4Norm,
  ylab = "", xlab = "",
  main = TeX(r'($\bar{\textit{NHR}}_{E4}$)'),
  ggtheme = my_theme1
)

n_HRE4Norm <- sum(!is.na(Qlevel_Simpl_Stress$HR.E4Norm))
HR_E4_stress_qq_all <- HR_E4_stress_qq_all + annotate("text", x = 0, y = Inf, hjust = 0.5, vjust = 1.5,  parse = TRUE, size = 5,
                   label = paste0("~italic(n)", " == ", n_HRE4Norm)
                   )

# Plot for HR.IBINorm
NHRV_stress_qq_all <- ggqqplot(Qlevel_Simpl_Stress$HRVNorm,
  ylab = "", xlab = "",
  main = TeX(r'(\bar{\textit{NHRV}})'),
  ggtheme = my_theme1
)

n_HRVNorm <- sum(!is.na(Qlevel_Simpl_Stress$HRVNorm))
NHRV_stress_qq_all <- NHRV_stress_qq_all + annotate("text", x = 0, y = Inf, hjust = 0.5, vjust = 1.5,  parse = TRUE, size = 5,
                   label = paste0("~italic(n)", " == ", n_HRVNorm)
                   )

grid.arrange(PP_stress_qq_all ,HR_E4_stress_qq_all, HR_AW_stress_qq_all,NHRV_stress_qq_all, ncol = 4)

```





## S002 - Stress Threshold Visualization, QQPlots, Table
```{r stress_threshold_viz_t001, echo=FALSE, fig.height=10, fig.width=7}
library(qqplotr)

# PP_unit <- "°C$^2$"
# HR_unit = "BPM" # both HR E4 and AW are in BPM
# HRV_unit = "s"

# # build the full y‐label string
# pp_y_lab <- sprintf("$\\bar{\\Delta \\textit{EDA}}_{f}$ \\[%s\\]", PP_unit)
# hre4_y_lab = sprintf("$\\bar{\\Delta \\textit{HR}}_{E4 }$ [%s]", HR_unit)
# hraw_y_lab = sprintf("$\\bar{\\Delta \\textit{HR}}_{AW }$ [%s]", HR_unit)
# hrv_y_lab = sprintf("$\\bar{\\Delta \\textit{HRV}}$ [%s]", HRV_unit)

# All variables are scaled. 
PP_unit <- "scaled"
HR_unit = "scaled" 
HRV_unit = "scaled"

# build the full y‐label string
pp_y_lab <- sprintf("$\\bar{ \\textit{NFP}}$ ")
pp_y_lab <- sprintf("$\\bar{ \\textit{NFP}}$ ")
hraw_y_lab = sprintf("$\\bar{ \\textit{NHR}}_{AW }$ ")
hre4_y_lab = sprintf("$\\bar{ \\textit{NHR}}_{E4 }$ ")
hrv_y_lab = sprintf("$\\bar{ \\textit{NHRV}}$ ")



mycolors_stress <- c(NS = "green", S = "red")

PID_num <- 2
PID <- sprintf("S%03d", PID_num)

Qlevel_Simpl_Stress_PID <- Qlevel_Simpl_Stress %>%
  filter(ParticipantID %in% PID)


ylims_pID <- c(0, 4)

library(grid)   # for unit()

PP_stress_hist <- Qlevel_Simpl_Stress_PID %>%
  #mutate(PPNorm_mean = mean(PPNorm, na.rm = TRUE)) %>%
  ggplot(aes(x = PPNorm, fill = Stress.pp)) +
    geom_histogram(position = "dodge") +
    scale_fill_manual(
      values = alpha(mycolors_stress, 0.9),
      name   = sprintf("S%03d", PID_num),
      labels = c("RLS", "RHS"),
      guide  = guide_legend(
        keywidth  = unit(1.2, "cm"),  # widen each key
        keyheight = unit(0.5, "cm"),  # (optional) adjust height
        nrow = 1                      # keep items in one row
      )
    ) +
    geom_vline(aes(xintercept = PPNorm_mean),
               color    = "blue",
               linetype = 3,
               linewidth = 1) +
    labs(y = TeX(pp_y_lab), x = NULL) +
    my_theme1 +
    theme(
      strip.background   = element_rect(fill = "white", color = "black"),
      legend.title       = element_text(size = 14),
      legend.text        = element_text(size = 14),
      legend.spacing.x   = unit(1, "cm"),  # extra space between items
    )



HR_AW_stress_hist <- Qlevel_Simpl_Stress_PID %>%
  #filter(ParticipantID %in% PID) %>%
  ggplot(aes(x = HR.AWNorm, fill = Stress.hraw)) +
  scale_fill_manual(values = alpha(mycolors_stress, 0.9)) +
  #scale_y_continuous(limits = ylims_pID, guide = "none") + # "none" removes the y-axis ticks and labels
  scale_y_continuous(limits = ylims_pID) + # "none" removes the y-axis ticks and labels
   #geom_histogram( position = "dodge", binwidth = 0.05) +
  geom_histogram(position = "dodge") +
  #  facet_wrap(~ParticipantID, ncol = 1) +
  my_theme1 +
  labs(
    y = TeX(hraw_y_lab),
    x = "", title = NULL
  ) +
  geom_vline(aes(xintercept = HR.AWNorm_mean), color = "blue", linetype = 3, linewidth = 1)



HR_E4_stress_hist <- Qlevel_Simpl_Stress_PID %>%
  #filter(ParticipantID %in% PID) %>%
  ggplot(aes(x = HR.E4Norm, fill = Stress.hre4)) +
  scale_fill_manual(values = alpha(mycolors_stress, 0.9)) +
  scale_y_continuous(limits = ylims_pID) + # "none" removes the y-axis ticks and labels
  # geom_histogram( position = "dodge", binwidth = 1) +
  geom_histogram(position = "dodge") +
  #  facet_wrap(~ParticipantID, ncol = 1) +
  my_theme1 +
  labs(
    y = TeX(hre4_y_lab),
    x = "", title = NULL
  ) +
  geom_vline(aes(xintercept = HR.E4Norm_mean), color = "blue", linetype = 3, linewidth = 1)





NHRV_stress_hist <-  Qlevel_Simpl_Stress_PID %>%
  #filter(ParticipantID %in% PID) %>%
  ggplot(aes(x = HRVNorm, fill = Stress.nhrv)) +
  scale_fill_manual(values = alpha(mycolors_stress, 0.9)) +
  geom_histogram(position = "dodge") +
  my_theme1 +
  labs(
    y = TeX(hrv_y_lab),
    x = "", title = NULL
  ) +
  geom_vline(aes(xintercept = HRVNorm_mean), color = "blue", linetype = 3, linewidth = 1)


 # PID_hists <- ggarrange(PP_stress_hist,HR_AW_stress_hist, HR_E4_stress_hist, NHRV_stress_hist, ncol = 4, common.legend = TRUE, legend = "top")
 
 



# Plot for PPNorm
PP_stress_qq <- ggqqplot(Qlevel_Simpl_Stress_PID$PPNorm,
  ylab = "", xlab = "",
  #main = TeX(r'($\bar{\Delta \textit{EDA}}_{f}$ [°C$^2$])'),
  ggtheme = my_theme1
)

n <- sum(!is.na(Qlevel_Simpl_Stress_PID$PPNorm))
PP_stress_qq <- PP_stress_qq + annotate("text", x = 0, y = Inf, hjust = 0.5, vjust = 1.5,  parse = TRUE, size = 5,
                   label = paste0("~italic(n)", " == ", n)
                   )
  
  
# Plot for HR.E4
HRAW_stress_qq <- ggqqplot(Qlevel_Simpl_Stress_PID$HR.AWNorm,
  ylab = "", xlab = "",
  #main = TeX(r'(\bar{$\Delta\textit{HR}}_{E4 }$  \[BPM\])'),
  ggtheme = my_theme1
)


n <- sum(!is.na(Qlevel_Simpl_Stress_PID$HR.AWNorm))
HRAW_stress_qq <- HRAW_stress_qq + annotate("text", x = 0, y = Inf, hjust = 0.5, vjust = 1.5,  parse = TRUE, size = 5,
                   label = paste0("~italic(n)", " == ", n)
                   )
  


# Plot for HR.E4
HRE4_stress_qq <- ggqqplot(Qlevel_Simpl_Stress_PID$HR.E4Norm,
  ylab = "", xlab = "",
  #main = TeX(r'(\bar{$\Delta\textit{HR}}_{E4 }$  \[BPM\])'),
  ggtheme = my_theme1
)

n <- sum(!is.na(Qlevel_Simpl_Stress_PID$HR.E4Norm))
HRE4_stress_qq <- HRE4_stress_qq + annotate("text", x = 0, y = Inf, hjust = 0.5, vjust = 1.5,  parse = TRUE, size = 5,
                   label = paste0("~italic(n)", " == ", n)
                   )


# Plot for HR.IBINorm
NHRV_stress_qq <- ggqqplot(Qlevel_Simpl_Stress_PID$HRVNorm,
  ylab = "", xlab = "",
  #main = TeX(r'(\bar{\textit{NHRV}} [s])'),
  ggtheme = my_theme1
)

n <- sum(!is.na(Qlevel_Simpl_Stress_PID$HRVNorm))
NHRV_stress_qq <- NHRV_stress_qq + annotate("text", x = 0, y = Inf, hjust = 0.5, vjust = 1.5,  parse = TRUE, size = 5,
                   label = paste0("~italic(n)", " == ", n)
                   )


final <- ggpubr::ggarrange(
  # row1
  PP_stress_hist,  PP_stress_qq,
  # row2
  HR_AW_stress_hist, HRAW_stress_qq,
  # row3
  HR_E4_stress_hist, HRE4_stress_qq,
  # row4
  NHRV_stress_hist,  NHRV_stress_qq,

  ncol           = 2,
  nrow           = 4,
  common.legend  = TRUE,
  legend         = "top"     # ← puts legend above the whole grid
)


final

if (is_save) {
  ggsave(
  filename = sprintf("%sFigure7.pdf", plot_dir),
    plot     = final,
    width    = 7,
    height   = 10,
    dpi      = 300
  )
}

```








# Stress MODELs 
*Qlevel stress labeling (Mean is threshold) on PP, HR_E4, HR_AW , HRV Channel*

```{r include=FALSE}
names(Qlevel_Simpl_Stress)
str(Qlevel_Simpl_Stress)

Qlevel_Stress_Simple <- Qlevel_Simpl_Stress %>%
  rename(
    Participant = ParticipantID,
    QType = QType,
    QName = Question.Name,
    Stress.Pp = Stress.pp,
    Stress.HrE4 = Stress.hre4, # HRE4
    Stress.HrAW = Stress.hraw, # HRAW
    Stress.Hrv = Stress.nhrv # HRVNorm
  )

names(Qlevel_Stress_Simple)
```

### Correlation Matrix - Stress Labels and quantitative variables
```{r fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
# colnames(Qlevel_Stress_Simple)
# str(Qlevel_Stress_Simple)
library(ggcorrplot)
reduced_data <-
  subset(Qlevel_Stress_Simple, select = c(
    Perspiration,
    HR.E4,
    HR.AW,
    Stress.Pp,
    Stress.HrE4,
    Stress.HrAW,
    Stress.Hrv
  )) #


#colSums(is.na(reduced_data))

model.matrix(~., data = reduced_data) %>%
  cor(use = "everything") %>%
  ggcorrplot(show.diag = FALSE, type = "lower", lab = TRUE) +
  ggtitle("Correlation Matrix with Best HR")
```



# Model 1 - PP_Stress - PPNorm Logistic Regression Mixed Effects Model
## Correlation Model Matrix

```{r fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
reduced_data <- subset(Qlevel_Stress_Simple, select = c(Grade, Gender, QType, SAI, PPNorm, Stress.Pp))

model.matrix(~., data = reduced_data) %>%
  cor(use = "everything") %>%
  ggcorrplot(show.diag = FALSE, type = "lower", lab = TRUE)
```

## Full Model
```{r echo=FALSE, message=FALSE, warning=FALSE}

# Fit the model
Stress.PP.fit.full <- glmer(Stress.Pp ~ 1 + Grade + Gender + QType + scale(SAI) + (1 | Participant), data = Qlevel_Stress_Simple, family = binomial(link = "logit"))

summary(Stress.PP.fit.full)

summ(Stress.PP.fit.full, digits = 4)
```


## Remove Gender

```{r warning=FALSE}
# Fit the model
Stress.PP.fit.fm <- glmer(Stress.Pp ~ 1 +  Grade + QType + scale(SAI) + (1 | Participant), data = Qlevel_Stress_Simple, family = binomial(link = "logit"))

summary(Stress.PP.fit.fm)
summ(Stress.PP.fit.fm, digits = 4)
```

## Remove Grade - Optimal PP Stress Model

```{r warning=FALSE}
# Fit the model
Stress.PP.fit.fm <- glmer(Stress.Pp ~ 1 +  QType + scale(SAI) + (1 | Participant), data = Qlevel_Stress_Simple, family = binomial(link = "logit"))

summary(Stress.PP.fit.fm)
summ(Stress.PP.fit.fm, digits = 4)
```


## Remove SAI ? 
*No, AIC is getting bigger*

```{r SAI test, warning=FALSE}
# Fit the model
Stress.PP.fit.fm_test <- glmer(Stress.Pp ~ 1 +  QType  + (1 | Participant), data = Qlevel_Stress_Simple, family = binomial(link = "logit"))

summary(Stress.PP.fit.fm_test)
summ(Stress.PP.fit.fm_test, digits = 4)
```



### Fixed Effects Visualization of Stress Model - PP
```{r fig.height=4.5, fig.width=7}
m.plot.stress_pp <- sjPlot::plot_model(Stress.PP.fit.fm,
  show.values = TRUE, show.p = TRUE,
  value.offset = 0.1,
  #axis.labels = c("QC[W]", "QC[A]"),
  title = ""
) + my_theme1

m.plot.stress_pp$layers[[4]]$aes_params$vjust <- (0.1)
m.plot.stress_pp$layers[[4]]$aes_params$hjust <- (-0.1)

m.plot.stress_pp
```




### Stress PP Final Model Predictors Plot

```{r echo=FALSE}
pp_final_grade.qt.pm <- fm_plot_func(Stress.PP.fit.fm, term = "QType" , ymin = 0.15, ymax = 0.7)
# Remove legend from main plot and add title
pp_final_grade.qt.pm <- pp_final_grade.qt.pm + 
  theme(legend.position = "none") + ggtitle(TeX(r'(Stress via \textit{$EDA_f$})'))

pp_final_sai.pm <- fm_plot_func(Stress.PP.fit.fm, term = "SAI", ymin = 0.15, ymax = 0.7)


# Arrange plot and legend together
final_plot <- cowplot::plot_grid(pp_final_grade.qt.pm,  pp_final_sai.pm, 
                                 ncol = 2, 
                                 rel_heights = c(4, 4))

final_plot = cowplot::plot_grid(final_plot, mylegend, nrow = 2, rel_heights = c(4, 1))

# Print the final plot
print(final_plot)
```



# Model 2 -  HRAW_Stress - HRAWNorm Logistic Regression Mixed Effects Model
## Correlation Model Matrix

```{r fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
reduced_data <- subset(Qlevel_Stress_Simple, select = c(Grade, Gender, QType, SAI, HR.AW, Stress.HrAW))

model.matrix(~., data = reduced_data) %>%
  cor(use = "everything") %>%
  ggcorrplot(show.diag = FALSE, type = "lower", lab = TRUE)
```

## Full Model
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Fit the model
Stress.HR.fit.full <- glmer(Stress.HrAW ~ 1 + Grade + Gender + QType + scale(SAI) + (1 | Participant), data = Qlevel_Stress_Simple, family = binomial(link = "logit"))

summary(Stress.HR.fit.full)

summ(Stress.HR.fit.full, digits = 4)
```

## Remove SAI

```{r}
# Fit the model
Stress.HRAW.fit.fm <- glmer(Stress.HrAW ~ 1 + Grade + Gender + QType + (1 | Participant), data = Qlevel_Stress_Simple, family = binomial(link = "logit"))

summary(Stress.HRAW.fit.fm)

summ(Stress.HRAW.fit.fm, digits = 4)
```

## Remove Gender

```{r}
# Fit the model
Stress.HRAW.fit.fm <- glmer(Stress.HrAW ~ 1 + Grade + QType + (1 | Participant), data = Qlevel_Stress_Simple, family = binomial(link = "logit"))

summary(Stress.HRAW.fit.fm)

summ(Stress.HRAW.fit.fm, digits = 4)
```


### Fixed Effects Visualization of Stress Model - HRAW
```{r fig.height=4.5, fig.width=7}
m.plot.stress_hr <- sjPlot::plot_model(Stress.HRAW.fit.fm,
  show.values = TRUE, show.p = TRUE,
  #axis.labels = c("QC[W]", "QC[A]"),
  value.offset = 0.1,
  title = ""
) + my_theme1 #+theme_bw()

m.plot.stress_hr$layers[[4]]$aes_params$vjust <- (0.1)
m.plot.stress_hr$layers[[4]]$aes_params$hjust <- (-0.1)

m.plot.stress_hr
```

\newpage

### Stress HRAW Final Model Predictors Plot

```{r fig.height=5, fig.width=6}
hr_aw_final_grade.qt.pm <- fm_plot_func(Stress.HRAW.fit.fm, term = "QType", ymin = 0.15, ymax = 0.7)
# Remove legend from main plot and add title
hr_aw_final_grade.qt.pm <- hr_aw_final_grade.qt.pm + theme(legend.position = "none") +
  ggtitle(TeX(r'(Stress via \textit{$HR AW$})'))



hr_aw_final_grade.pm <- fm_plot_func(Stress.HRAW.fit.fm, term = "Grade", ymin = 0.15, ymax = 0.7)
# Remove legend from main plot and add title
hr_aw_final_grade.pm <- hr_aw_final_grade.pm + theme(legend.position = "none") +
  ggtitle(TeX(r'(\textit{$Grade$})'))


# Arrange plot and legend together
final_plot_hr_aw_grid <- cowplot::plot_grid(hr_aw_final_grade.qt.pm,  hr_aw_final_grade.pm, 
                                 ncol = 2, 
                                 rel_heights = c(4, 4),
                                 align = "h") 

final_plot = cowplot::plot_grid(final_plot_hr_aw_grid, mylegend, nrow = 2, rel_heights = c(4, 1))

# Print the final plot
print(final_plot)


```

# Model 3 -  HRE4_Stress Stress - HRE4Norm Logistic Regression Mixed Effects Model
## Correlation Model Matrix

```{r fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
reduced_data <- subset(Qlevel_Stress_Simple, select = c(Grade, Gender, QType, SAI, HR.E4, Stress.HrE4))

model.matrix(~., data = reduced_data) %>%
  cor(use = "everything") %>%
  ggcorrplot(show.diag = FALSE, type = "lower", lab = TRUE)
```

## Logistic Regression Mixed Effects Model of Stress - HR E4
### Full Model
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Fit the model
Stress.HR.fit.full <- glmer(Stress.HrE4 ~ 1 + Grade + Gender + QType + scale(SAI) + (1 | Participant), data = Qlevel_Stress_Simple, family = binomial(link = "logit"))

summary(Stress.HR.fit.full)

summ(Stress.HR.fit.full, digits = 4)
```

## Remove SAI

```{r}
# Fit the model
Stress.HRE4.fit.fm <- glmer(Stress.HrE4 ~ 1 + Grade + Gender + QType  + (1 | Participant), data = Qlevel_Stress_Simple, family = binomial(link = "logit"))

summary(Stress.HRE4.fit.fm)

summ(Stress.HRE4.fit.fm, digits = 4)
```

## Remove Gender - Optimal HR E4 Stress Model

```{r}
# Fit the model
Stress.HRE4.fit.fm <- glmer(Stress.HrE4 ~ 1 + Grade  + QType  + (1 | Participant), data = Qlevel_Stress_Simple, family = binomial(link = "logit"))

summary(Stress.HRE4.fit.fm)

summ(Stress.HRE4.fit.fm, digits = 4)
```




### Fixed Effects Visualization of Stress Model - HR E4

```{r fig.height=4.5, fig.width=7}
m.plot.stress_hr <- sjPlot::plot_model(Stress.HRE4.fit.fm,
  show.values = TRUE, show.p = TRUE,
  #axis.labels = c("QC[W]", "QC[A]"),
  value.offset = 0.1,
  title = ""
) + my_theme1 #+theme_bw()

m.plot.stress_hr$layers[[4]]$aes_params$vjust <- (0.1)
m.plot.stress_hr$layers[[4]]$aes_params$hjust <- (-0.1)

m.plot.stress_hr
```

\newpage

### Stress HRE4 Final Model Predictors Plot

```{r fig.height=5, fig.width=6}
hr_e4_final_grade.qt.pm <- fm_plot_func(Stress.HRE4.fit.fm, term = "QType", ymin = 0.15, ymax = 0.7)
# Remove legend from main plot and add title
hr_e4_final_grade.qt.pm <- hr_e4_final_grade.qt.pm + theme(legend.position = "none") +
  ggtitle(TeX(r'(Stress via \textit{$HR E4$})'))


hr_e4_final_grade.pm <- fm_plot_func(Stress.HRE4.fit.fm, term = "Grade", ymin = 0.15, ymax = 0.7)

# Remove legend from main plot and add title
hr_e4_final_grade.pm <- hr_e4_final_grade.pm + theme(legend.position = "none") +
  ggtitle(TeX(r'(\textit{$Grade$})'))


# Arrange plot and legend together
final_plot <- cowplot::plot_grid(hr_e4_final_grade.qt.pm,  hr_e4_final_grade.pm, 
                                 ncol = 2, 
                                 rel_heights = c(4, 4))

final_plot = cowplot::plot_grid(final_plot, mylegend, nrow = 2, rel_heights = c(4, 1))

# Print the final plot
print(final_plot)



```


# Model 4 -  HRV_Stress - HRVNorm Logistic Regression Mixed Effects Model

## Correlation Model Matrix

```{r fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
reduced_data <- subset(Qlevel_Stress_Simple, select = c(Grade, Gender, QType, SAI, HR.AW, Stress.Hrv))

model.matrix(~., data = reduced_data) %>%
  cor(use = "everything") %>%
  ggcorrplot(show.diag = FALSE, type = "lower", lab = TRUE)
```

## Full Model
```{r warning=FALSE}

# Fit the model
Stress.HRV.fit.full <- glmer(Stress.Hrv ~ 1 + Grade + Gender + QType + scale(SAI) + (1 | Participant), data = Qlevel_Stress_Simple, family = binomial(link = "logit"))


summary(Stress.HRV.fit.full)
summ(Stress.HRV.fit.full, digits = 4)
```

## Remove SAI
```{r warning=FALSE}
# Fit the model
Stress.HRV.fit.fm <- glmer(Stress.Hrv ~ 1 + Grade + Gender + QType  + (1 | Participant), data = Qlevel_Stress_Simple, family = binomial(link = "logit"))


summary(Stress.HRV.fit.fm)
summ(Stress.HRV.fit.fm, digits = 4)
```

## Remove Gender - Optimal HRV Stress Model
```{r warning=FALSE}
# Fit the model
Stress.HRV.fit.fm <-glmer(Stress.Hrv ~ 1 + Grade + QType  + (1 | Participant), data = Qlevel_Stress_Simple, family = binomial(link = "logit"))

summary(Stress.HRV.fit.fm)
summ(Stress.HRV.fit.fm, digits = 4)
```

### Fixed Effects Visualization of Stress Model - NHRV
```{r fig.height=4.5, fig.width=7}
m.plot.stress_hrv <- sjPlot::plot_model(Stress.HRV.fit.fm,
  show.values = TRUE, show.p = TRUE,
  #axis.labels = c("QC[W]", "QC[A]", "SAI"),
  value.offset = 0.1,
  title = ""
) + my_theme1 #+theme_bw()

m.plot.stress_hrv$layers[[4]]$aes_params$vjust <- (0.1)
m.plot.stress_hrv$layers[[4]]$aes_params$hjust <- (-0.1)

m.plot.stress_hrv
```

\newpage
### Stress Hrv Final Model Predictors Plot

```{r fig.height=5, fig.width=6}
hrv_final_grade.qt.pm <- fm_plot_func(Stress.HRV.fit.fm, term = "QType", ymin = 0.15, ymax = 0.7)
# Remove legend from main plot and add title
hrv_final_grade.qt.pm <- hrv_final_grade.qt.pm + theme(legend.position = "none") +
  ggtitle(TeX(r'(Stress via \textit{$HRV$})'))


hrv_final_grade.pm <- fm_plot_func(Stress.HRV.fit.fm, term = "Grade", ymin = 0.15, ymax = 0.7)

# Remove legend from main plot and add title
hrv_final_grade.pm <- hrv_final_grade.pm + theme(legend.position = "none") +
  ggtitle(TeX(r'(\textit{$Grade$})'))


# Arrange plot and legend together
final_plot <- cowplot::plot_grid(hrv_final_grade.qt.pm,  hrv_final_grade.pm, 
                                 ncol = 2, 
                                 rel_heights = c(4, 4))

final_plot = cowplot::plot_grid(final_plot, mylegend, nrow = 2, rel_heights = c(4, 1))

# Print the final plot
print(final_plot)


```



# Logistic-Regression-StressModels

```{r 2-Logistic-Regression-Plots, echo=FALSE, fig.height=12, fig.width=12}
# QType, Grade, SAI

pp_final_grade.qt.pm <- pp_final_grade.qt.pm + ggtitle(TeX("\\textit{QTYPE}"))
pp_final_sai.pm <- pp_final_sai.pm + ggtitle( TeX("\\textit{$SAI$}"))
hr_aw_final_grade.qt.pm <- hr_aw_final_grade.qt.pm + ggtitle("") 
hr_aw_final_grade.pm <- hr_aw_final_grade.pm +ggtitle( TeX("\\textit{QGRADE}")) + theme()
hr_e4_final_grade.qt.pm <- hr_e4_final_grade.qt.pm + ggtitle("")
hr_e4_final_grade.pm <- hr_e4_final_grade.pm + ggtitle("")
hrv_final_grade.qt.pm <- hrv_final_grade.qt.pm + ggtitle("")
hrv_final_grade.pm <- hrv_final_grade.pm + ggtitle("")


#PP row
row1 <- cowplot::plot_grid(
  pp_final_grade.qt.pm, pp_final_sai.pm,
  nrow = 1,
  scale = c(.97, .97),
  labels = c("b1", ""),
  label_size = 20
)

#HR AW row
row2 <- cowplot::plot_grid(
  hr_aw_final_grade.qt.pm, hr_aw_final_grade.pm,
  nrow = 1,
  scale = c(.97, .97),
  labels = c("b2", ""),
  label_size = 20
)

#HR E4 row
row3 <- cowplot::plot_grid(
  hr_e4_final_grade.qt.pm, hr_e4_final_grade.pm,

  nrow = 1,
  scale = c(.97, .97),
  labels = c("b3", ""),
  label_size = 20
)

# HRV row
row4 <- cowplot::plot_grid(
hrv_final_grade.qt.pm, hrv_final_grade.pm, 
  nrow = 1,
  scale = c(.97, .97),
  labels = c("b4", ""),
  label_size = 20
)


# --- 2. assume you already have this from before: ---
final_5M <- cowplot::plot_grid(
  row1, row2, row3, row4, mylegend,
  nrow = 5,
  rel_heights = c(1, 1, 1, 1, 0.1)
)


#final_5M 


```



```{r echo=FALSE, fig.height=12, fig.width=10}
library(cowplot)

# # 1. build the top header
# title_row <- ggdraw() +
#   draw_label("QTYPE", x = 1.3/7, y = 0.5, fontface = "bold", hjust = 0.5) +
#   draw_label("QGRADE",         x = 3/6, y = 0.5, fontface = "bold", hjust = 0.5) +
#   draw_label("SAI",           x = 5/6, y = 0.5, fontface = "bold", hjust = 0.5) +
#   theme_void()

# 2. build the right‐hand strip



# define band‐height and gap
h <- 0.20   # 20% of panel height
g <- 0.05   # 5% gap between bands

right_strip <- ggdraw() +
  # PP band: spans y = 0.80 → 1.00  
  draw_grob(
    grob   = grid::rectGrob(gp = grid::gpar(fill = "grey90", col = NA)),
    x      = 0,
    y      = 1 - h,
    width  = 1,
    height = h
  ) +
  # HR E4 band: spans y = 0.55 → 0.75  
  draw_grob(
    grob   = grid::rectGrob(gp = grid::gpar(fill = "grey90", col = NA)),
    x      = 0,
    y      = 1 - (2*h + g),
    width  = 1,
    height = h
  ) +
  # HR AW band: spans y = 0.30 → 0.50  
  draw_grob(
    grob   = grid::rectGrob(gp = grid::gpar(fill = "grey90", col = NA)),
    x      = 0,
    y      = 1 - (3*h + 2*g),
    width  = 1,
    height = h
  ) +
  # HRV band: spans y = 0.05 → 0.25  
  draw_grob(
    grob   = grid::rectGrob(gp = grid::gpar(fill = "grey90", col = NA)),
    x      = 0,
    y      = 1 - (4*h + 3*g),
    width  = 1,
    height = h
  ) +
  # labels on top of each band
  draw_label("FP",    x = 1, y = 0.90, angle = -90, fontface = "bold", vjust = 2) +
  draw_label("HR AW", x = 1, y = 0.65, angle = -90, fontface = "bold", vjust = 2) +
  draw_label("HR E4", x = 1, y = 0.40, angle = -90, fontface = "bold", vjust = 2) +
  draw_label("HRV",   x = 1, y = 0.15, angle = -90, fontface = "bold", vjust = 2) +
  theme_void()


# 3. glue grid + strip side‐by‐side
middle <- cowplot::plot_grid(
  final_5M,
  right_strip,
  ncol        = 2,
  rel_widths  = c(0.95, 0.05)
)

```

```{r echo=FALSE, fig.height=11, fig.width=8}

middle
#Save the final_5M plot
ggsave(
  filename = sprintf("%sFigure12.pdf", plot_dir), # 2-Logistic-Regression-Plots
  
  plot = middle,
  width = 8,
  height = 11,
  dpi = 300
)
```

\newpage

# Paper Table II

```{r}
summ(Stress.PP.fit.fm, digits = 3)$model@call
M1_table = summ(Stress.PP.fit.fm, digits = 3)$coeftable

summ(Stress.HRAW.fit.fm, digits = 3)$model@call
M2_table = summ(Stress.HRAW.fit.fm, digits = 3)$coeftable

summ(Stress.HRE4.fit.fm, digits = 3)$model@call
M3_table = summ(Stress.HRE4.fit.fm, digits = 3)$coeftable


summ(Stress.HRV.fit.fm, digits = 3)$model@call
M4_table = summ(Stress.HRV.fit.fm, digits = 3)$coeftable


merge <- rbind(M1_table, M2_table, M3_table, M4_table)


```


```{r model-table, include=FALSE, results='asis'}
library(dplyr)
library(purrr)
library(knitr)

# 1) Put your models in a named list
models <- list(
  fEDA  = Stress.PP.fit.fm,
  HR_AW = Stress.HRAW.fit.fm,
  HR_E4 = Stress.HRE4.fit.fm,
  HRV   = Stress.HRV.fit.fm
)

# 2) extract each summary(...$coefficients) into a data.frame
coef_dfs <- lapply(models, function(mod) {
  co <- summ(mod, digits = 3)$coeftable
  #as.data.frame(co, stringsAsFactors = FALSE)
  as.data.frame(co, stringsAsFactors = FALSE) #%>% dplyr::select(-4)
})


# 1) figure out every predictor that appears in any model
all_preds <- unique(unlist(lapply(coef_dfs, rownames)))

# 2) for each df, turn rownames into a column, 
#    re-order to 'all_preds', and then put rownames back
aligned <- lapply(coef_dfs, function(df) {
  df2 <- as.data.frame(df, stringsAsFactors=FALSE)
  df2$Predictor <- rownames(df2)
  
  # reorder (and insert NA rows for missing preds)
  df2 <- df2[match(all_preds, df2$Predictor), , drop=FALSE]
  
  # restore rownames
  rownames(df2) <- all_preds
  df2
})

# 4) now cbind them
merged <- do.call(cbind, aligned)

# 5) restore a single Predictor column in front
merged <- cbind(Predictor = rownames(merged), merged, row.names=NULL)


# Select all columns that end with ".Est." and drop them
Est_all <- merged %>% dplyr::select(Predictor,ends_with(".Est."))
SE_all <- merged %>% dplyr::select(Predictor,ends_with(".S.E."))
t_all <- merged %>% dplyr::select(Predictor,ends_with(".z val."))
p_all <- merged %>% dplyr::select(Predictor,ends_with(".p"))

paper_merged <- cbind(Est_all, SE_all[, -1], t_all[, -1], p_all[, -1])
```


```{r merged-table, results='asis', echo=FALSE}
# 2) Build your header labels
stat_labels  <- c("Est", "S.E.", "z", "p")
# bottom row: model names repeated under each stat
model_names  <- c("fEDA", "HRAW", "HRE4", "HRV")
var_labels   <- rep(model_names, times = length(stat_labels))

# define a very light and a medium light gray
light_gray  <- if (knitr::is_latex_output()) "gray!25" else "#E6E6E6"
medium_gray <- if (knitr::is_latex_output()) "gray!50" else "#CCCCCC"


paper_merged %>%  
  mutate(
    across(
      ends_with(".p"),
      ~ round(., 3)
    )
  ) %>%
  mutate(
    across(
      ends_with(".p"),
      ~ format.pval(., digits = 3, eps = 0.001)
    )
  ) %>%  mutate(
    across(
      ends_with(".z val"),
      ~ round(., 3)
    )
  ) %>%  kable(
  digits = 3,
  format          = "html",
  #format          = "latex",
  booktabs        = TRUE,
  escape          = TRUE,
  table.placement = "H",
  col.names       = c("Predictor", var_labels),
  align           = c("l", rep("r", length(var_labels)))
) %>%
  add_header_above(
    header = c(
      " "    = 1,
      "Coefficient $b.$"    = 4,
      "$S.E.$" = 4,
      "$z$ value" = 4,
      "Pr(>$|z|$)"  = 4
    ),
    bold = TRUE
  ) %>%
  column_spec(c(3,7, 11,15),   background = light_gray) %>% # myGray
  column_spec(c(5, 9, 13 ,17),   background = medium_gray) %>%  # gray 0.9
  column_spec(c(4,6,8),   background = "white")    %>%
  kable_styling(
    latex_options = c("hold_position","scale_down"),
    font_size     = 11
  )
```



