---
title: "Affective Math Multi linear Regression Mixed Effects"
author: "Fettah Kiran"
subtitle: "Valence Models and Performance Models | N = 50"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    theme: united
    number_sections: true 
    mathjax: default
  pdf_document: 
    toc: true
    number_sections: true 
    keep_tex: true
header-includes:
  - \usepackage[table]{xcolor}
  - \definecolor{myGray}{gray}{0.8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

------------------------------------------------------------------------

*Notes:* 

- Qlevel data is created by grouping the raw trial‑level data by participant, question type, and question name, and then computing the mean outcome within each group.
- All inferential analyses were carried out with linear mixed‑effects models that include a participant‑centered random intercept to account for between‑subject variability.

`Reference for Question Type: "V"`

------------------------------------------------------------------------

```{r include=FALSE}
rm(list = ls())
dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(dir)
getwd()
```

\newpage

```{r include=FALSE}
source("requirements.R")
```


```{r SpecialThemes, message=FALSE, warning=FALSE}


# Load custom functions
#browseURL("fm_plot_func.R")
source("fm_plot_func.R")

# options(digits=3)
theme_set(theme_classic()) # set the theme to classic
theme_update(plot.title = element_text(hjust = 0.5)) # center the title

my_theme_bold.italic <- my_theme + theme(text = element_text(size = 14, face = "bold"))

data_dir = "../data/processed/" # data directory
plot_dir = "../figures/" # plot directory

is_save <- TRUE
```

\newpage

```{r readRawData, include=FALSE}
N <- 50


file = sprintf("%sTAFFC_Qlevel_Data_N%s.csv", data_dir, N)

Qlevel = read.csv(file, header = TRUE, sep = ",", stringsAsFactors = T)


names(Qlevel)

Qlevel$Question.Type <- factor(Qlevel$Question.Type, levels = c("V", "A", "W"))
Qlevel$Gender <- relevel(factor(Qlevel$Gender), ref = "M")
Qlevel$Grade <- relevel(factor(Qlevel$Grade), ref = "0")


```



# Model 5 - Performance Model

```{r include=FALSE}

names(Qlevel)

tmpD <- Qlevel  %>%
  dplyr::select(ParticipantID, Question.Name, Question.Type,Gender, Perspiration, PPNorm, #PPlogNorm,
         HR.E4,HR.AW, HR.E4Norm, 
#HRE4PerfNorm, 
         HR.AWNorm, HRV.IBI, HRVNorm, SAI,
         QTime, QOrder,QNumber, Grade)

# Update list according to the variable names in the data
VarNames <- c(
  "S", "QName", "QType", "Gender", "PPMean", "PPNorm", 
  #"PPlogNorm",
  "HRE4Mean", "HRAWMean", "HRE4Norm", 
#"HRE4PerfNorm",
  "HRAWNorm", "HRVIBIMean", "HRVNorm", "SAI",
  "QSolTime", "QOrder", "QNumber", "Grade"
)


names(tmpD) <- VarNames

M5_data <- tmpD %>%
  dplyr::select(S, Grade, Gender, QType, QSolTime, PPNorm, HRE4Norm, HRAWNorm, HRVNorm, HRVIBIMean, SAI, QName)

```



## Collinearity Check

```{r fig.height=7, fig.width=7, message=FALSE, warning=FALSE}
library(ggcorrplot)

# Pairwise.complete.obs
reduced_data <- subset(M5_data, select = c(-Grade, -QName, -S, -HRVNorm, -HRVIBIMean))
# str(reduced_data)
model.matrix(~., data = reduced_data) %>%
  cor(use = "everything") %>%
  ggcorrplot(show.diag = FALSE, type = "lower", lab = TRUE)
```

## Full Model

```{r echo=FALSE}

M5.fit.full <-
  glmer(Grade ~ 1 + Gender + QType + scale(QSolTime) + scale(PPNorm) + scale(SAI) + (1 | QName), family = binomial, data = M5_data)

summary(M5.fit.full, digits = 3)
summ(M5.fit.full, digits = 3)
```

\newpage

## Manual Optimization based on the p-value

### Remove QSolTime

```{r echo=FALSE}
M5.fit.fm <-
  glmer(Grade ~ 1 + Gender + QType + scale(PPNorm) + scale(SAI) + (1 | QName), family = binomial, data = M5_data)

summary(M5.fit.fm, digits = 3)
summ(M5.fit.fm, digits = 3)
```

### Remove Gender - Scaled Optimal Model

```{r echo=FALSE}
M5.fit.fm <-
 glmer(Grade ~ 1 + QType + scale(PPNorm) + scale(SAI) + (1 | QName), family = binomial, data = M5_data)

summary(M5.fit.fm)
summ(M5.fit.fm, digits = 3)
```


\newpage

## Plot Final Model Predictors

```{r fig.height=5, fig.width=6}
gradePP_sai.pm <- ggpredict(M5.fit.fm, "SAI [all]") %>%
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2) +
  geom_line(colour = "red", size = 2) +
  geom_vline(
    xintercept = mean(tmpD$SAI, na.rm = TRUE),
    linetype = "dashed",
    color = "gray",
    size = 1
  ) +
  scale_y_continuous(
    limits = c(0.1, 0.9),
    breaks = seq(0.1, 0.9, by = 0.2) 
  ) +
  my_theme_pred_quant + 
  labs(
    x = "",
    y = "",
    title = TeX("SAI")
  )

pp_y_lab <- sprintf("$\\bar{ \\textit{NFP}}$")

gradePP_pp.fm <- ggpredict(M5.fit.fm, "PPNorm [all]") %>%
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2) +
  geom_line(colour = "cyan", size = 2) +
  geom_vline(
    xintercept = mean(tmpD$PPNorm, na.rm = TRUE),
    linetype = "dashed",
    color = "gray",
    size = 1
  ) +
  scale_y_continuous(
    limits = c(0.1, 0.9),
    breaks = seq(0.1, 0.9, by = 0.2) # Sets y-axis breaks to increase by 0.1
  ) +
  my_theme_pred_quant + 
  labs(
    x = "",
    y = "",
    title = TeX(pp_y_lab)
  )


# Question Type
gradePP.qt.pm <- ggpredict(M5.fit.fm,
  terms = c("QType")
) %>%
  mutate(group = as.factor(c("1", "2", "3"))) %>%
  drop_na() %>% # check # of levels you've
  gather(key = "key", value = "value", conf.low, conf.high) %>%
  ggplot() +
  geom_line(aes(x = x, y = value, color = group), size = 2) +
  geom_point(aes(x = x, y = predicted, color = group, size = 2)) +
  my_theme_pred +
  scale_y_continuous(
    limits = c(0.1, 0.9),
    breaks = seq(0.1, 0.9, by = 0.2) # Sets y-axis breaks to increase by 0.1
  ) +
  scale_color_manual(values = c("gray", "black", "black")) +
  my_theme1 +
  theme(
    axis.text.x = element_text(size = 16, face = "bold.italic"),
    axis.text.y = element_text(size = 16, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
  ) +
  labs(
    title = TeX("QTYPE"),
    x = "",
    y = TeX(" \\textit{P(QGRADE)}$"),
    y = NULL)
  

# gradePP.qt.pm
```

```{r echo=FALSE}
p12.ap <- cowplot::plot_grid(
  gradePP.qt.pm,gradePP_sai.pm, gradePP_pp.fm,
  nrow = 1,
  scale = c(.97, .97, .97),
  labels = c("a", "b" , "c"),
  label_size = 20
)

p12.ap.legend <- cowplot::plot_grid(p12.ap,
  mylegend,
  nrow = 2,
  rel_heights = c(1, .1)
)



p12.ap.legend


# p34.st.sai <- cowplot::plot_grid(
#   gradePP.qt.pm,
#   nrow = 1,
#   scale = c(.97),
#   labels = c("b"),
#   label_size = 20
# )
# 
# 
# final.w.legend <- cowplot::plot_grid(p12.ap.legend, p34.st.sai,
#   nrow = 2,
#   rel_heights = c(1, 1)
# )
# 
# final.w.legend

```

## Fixed Effects Visualization of Grade Model

```{r echo=FALSE}
sjPlot::plot_model(M5.fit.fm, "est",
  show.values = TRUE, show.p = TRUE, sort = TRUE,
  value.offset = 0.2,
  title = ""
) +
  theme(axis.text = element_text(size = 10))
```

\newpage



# Valence Qlevel data

```{r echo=FALSE, message=FALSE, warning=FALSE}

Valence.Qlevel <- Qlevel %>%
  dplyr::select(ParticipantID, Question.Name, Question.Type, Angry:Neutral) 

Valence.Qlevel$Question.Type <- factor(Valence.Qlevel$Question.Type, levels = c("V", "A", "W"))

#colSums(is.na(Valence.Qlevel)) # Check for NAs
 # Remove NAs
Valence.Qlevel <- na.omit(Valence.Qlevel)
#colSums(is.na(Valence.Qlevel)) # Check for NAs
print("Number of participants in Qlevel Valence data frame")
table(Valence.Qlevel$ParticipantID)
```


## Valence descriptives


### Qlevel 

```{r fig.height= 4.5, fig.width=7}
# Boxplot of Valence Qlevel by Question Type

long_data <- Valence.Qlevel %>%
  pivot_longer(cols = Angry:Neutral, names_to = "Emotion", values_to = "Probability") %>%
  arrange(ParticipantID, Question.Type)

long_data$Emotion <- factor(long_data$Emotion)


long_data$Question.Type <- factor(long_data$Question.Type, levels = c("A", "V", "W"))

emotion_labels <- c("Afraid", "Angry", "Disgusted", "Happy", "Neutral", "Sad", "Surprised")

long_data %>%
  mutate(n = n()) %>%
  ggplot(aes(x = Emotion, y = Probability * 100, fill = Emotion)) +
  geom_boxplot() +
  scale_fill_manual(
    values = c(
      "Angry" = "red",
      "Afraid" = "orange",
      "Disgusted" = "green",
      "Happy" = "yellow",
      "Neutral" = "grey",
      "Sad" = "blue",
      "Surprised" = "purple"
    ),
    name = "",
    labels = emotion_labels,
    guide = guide_legend(nrow = 1) # Put legend labels in one row
  ) +
  scale_x_discrete(labels = emotion_labels) +
  scale_y_continuous(labels = scales::label_number(), limits = c(0, 100)) +
  labs(
    title = TeX(paste0("Question Level | $\\textit{n}$ = ", N)),
    y = "Observations [%]", x = ""
  ) +
  my_theme1 +
  theme(legend.position = "none") # +
  # geom_text(aes(label = paste0("~italic(n)", " == ", n), y = 75),
  #   size = 4, vjust = -1, hjust = 0.75, parse = TRUE, angle = 90,
  #   position = position_dodge(width = 1)
  # )
```

### Valence Stack Plot - Figure 10a

```{r Valence_Qlevel_data, echo=FALSE, fig.height=7, fig.width=11}
long_data <- Valence.Qlevel %>%
  pivot_longer(cols = Angry:Neutral, names_to = "Emotion", values_to = "Probability") %>%
  arrange(ParticipantID, Question.Type)

long_data$Emotion <- factor(long_data$Emotion, levels = c("Angry", "Disgusted", "Afraid", "Happy", "Sad", "Surprised", "Neutral"))

long_data <- long_data %>%
  mutate(
    ID_and_Task = interaction(ParticipantID, Question.Type, sep = "_"),
    ParticipantID = factor(ParticipantID)
  ) # Ensure ParticipantID is a factor to maintain order

strip_labels <- c(
  "V" = "VIDEO",
  "A" = "ABSTRACT",
  "W" = "WORD"
)




rm(Valence_Qlevel_stack)
Valence_Qlevel_stack <- long_data %>%
  ggplot(aes(x = ParticipantID, y = Probability, fill = Emotion)) +
  geom_bar(stat = "identity", position = "fill") +
  facet_wrap(~Question.Type ~ .,
    scales = "free_y", nrow = 3,
    strip.position = "right",
    labeller = as_labeller(strip_labels)
  ) + 
  scale_fill_manual(
    values = c(
      "Angry" = "red",
      "Disgusted" = "green",
      "Afraid" = "orange",
      "Happy" = "yellow",
      "Sad" = "blue",
      "Surprised" = "purple",
      "Neutral" = "grey"
    ),
    name = "",
    labels = c("ANGRY", "DISGUSTED", "AFRAID", "HAPPY", "SAD", "SURPRISED", "NEUTRAL"),
    guide = guide_legend(nrow = 1) # Put legend labels in one row
  ) +
  labs(title = "", y = "", x = "") +
  my_theme1 +
  theme(
    #axis.text.x.bottom = element_text(angle = 60, hjust = 0.5),
    axis.text.x.bottom = element_text(angle = 75, hjust = 1),
    strip.background = element_rect(fill = "white", color = "black"), # Add border to facet labels
    # strip.text.x = element_text(size = 10, face = "bold"),,
    legend.text = element_text(size = 13),
    legend.position = "top"
  ) +  scale_x_discrete(guide = guide_axis(n.dodge = 2)) 


```

```{r Valence_Qlevel_stack, echo=FALSE, fig.height=7, fig.width=11}
Valence_Qlevel_stack

# Save the plot
#if (is_save == TRUE) {
  #f_path <- sprintf("%sValence_Qlevel_stack-1.pdf", plot_dir, N)
  f_path <- sprintf("%sFigure10a.pdf", plot_dir, N) #  Valence_Qlevel_stack-2
  ggsave(f_path, width = 11, height = 7)
#}

```

```{r echo=FALSE}
long_data2 <- Valence.Qlevel %>%
  pivot_longer(cols = Angry:Neutral, names_to = "Emotion", values_to = "Probability") %>%
  mutate(Question.Type = factor(Question.Type, levels = c("A", "V", "W")))

long_data2$Emotion <- factor(long_data2$Emotion, levels = c("Angry", "Disgusted", "Afraid", "Happy", "Sad", "Surprised", "Neutral"))

# Calculate the average probabilities and standard error
summary_data <- long_data2 %>%
  group_by(Question.Type, Emotion) %>%
  summarise(
    Average_Probability = mean(Probability, na.rm = TRUE),
    SE = sd(Probability, na.rm = TRUE) / sqrt(n())
  ) %>%
  filter(!is.na(Emotion)) %>%
  ungroup()


# Plotting the data
p3 <- summary_data %>%
  # filter(!(Emotion %in% c("Angry","Disgusted","Afraid", "Surprised"))) %>%
  ggplot(aes(x = Question.Type, y = Average_Probability, fill = Emotion)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = Average_Probability - SE - 0.001, ymax = Average_Probability + SE + 0.001), position = position_dodge(width = 0.9), width = 0.25) +
  scale_fill_manual(
    values = c(
      "Angry" = "red",
      "Disgusted" = "green",
      "Afraid" = "orange",
      "Happy" = "yellow",
      "Sad" = "blue",
      "Surprised" = "purple",
      "Neutral" = "grey"
    ),
    name = "",
    labels = c("Angry", "Disgusted", "Afraid", "Happy", "Sad", "Surprised", "Neutral"),
    guide = guide_legend(nrow = 1) # Put legend labels in one row
  ) +
  labs(
    title = "",
    y = "", x = ""
  ) +
  my_theme1 +
  theme(legend.position = "top") +  scale_y_continuous(labels = scales::percent) 

p3
```

```{r echo=FALSE, fig.height=10, fig.width=7}
my_theme1 <- theme(
  panel.grid = element_blank(),
  plot.title = element_text(hjust = 0.5),
  axis.text.x = element_text(size = 10, face = "bold.italic"),
  axis.text.y = element_text(size = 10, face = "bold"),
  strip.text = element_text(size = 14),
  legend.position = "none"
)

# width: change box plots width
fun_length <- function(x) {
  return(data.frame(y = median(x), label = paste0("n=", length(x))))
}


Valence.Qtype.boxplot <- Valence.Qlevel %>%
  ggplot(aes(x = Question.Type, y = Happy, fill = Question.Type)) +
  geom_boxplot(position = position_dodge(width = 0.9)) +
  ggtitle(bquote("Question Type")) +
  my_theme1 +
  labs(title = "Happy - Qlevel", x = "", y = "") +
  stat_summary(
    fun.data = n_fun, geom = "text", fun.y = median,
    parse = T, size = 5, vjust = -0.75, hjust = -0.75, angle = 90,
    position = position_dodge(width = 0.75)
  )
# Valence.Qtype.boxplot



Valence.Qtype.LogHappy <- Valence.Qlevel %>%
  ggplot(aes(x = Question.Type, y = log(Happy), fill = Question.Type)) +
  geom_boxplot(position = position_dodge(width = 0.9)) +
  ggtitle(bquote("Question Type")) +
  my_theme1 +
  labs(title = "Log Happy - Qlevel", x = "", y = "") +
  stat_summary(
    fun.data = n_fun, geom = "text", fun.y = median,
    parse = T, size = 5, vjust = -0.75, hjust = 1.25, angle = 90,
    position = position_dodge(width = 0.75)
  )
# Valence.Qtype.LogHappy


Valence.Qtype.Sad <- Valence.Qlevel %>%
  ggplot(aes(x = Question.Type, y = Sad, fill = Question.Type)) +
  geom_boxplot(position = position_dodge(width = 0.9)) +
  ggtitle(bquote("Question Type")) +
  my_theme1 +
  labs(title = "Sad - Qlevel", x = "", y = "") +
  stat_summary(
    fun.data = n_fun, geom = "text", fun.y = median,
    parse = T, size = 5, vjust = -0.75, hjust = -0.75, angle = 90,
    position = position_dodge(width = 0.75)
  )

# Valence.Qtype.Sad

Valence.Qtype.Neutral <- Valence.Qlevel %>%
  ggplot(aes(x = Question.Type, y = Neutral, fill = Question.Type)) +
  geom_boxplot(position = position_dodge(width = 0.9)) +
  ggtitle(bquote("Question Type")) +
  my_theme1 +
  labs(title = "Neutral - Qlevel", x = "", y = "") +
  stat_summary(
    fun.data = n_fun, geom = "text", fun.y = median,
    parse = T, size = 5, vjust = -0.75, hjust = -0.75, angle = 90,
    position = position_dodge(width = 0.75)
  )

# Valence.Qtype.Neutral

Valence.Qtype.LogNeutral <- Valence.Qlevel %>%
  ggplot(aes(x = Question.Type, y = log(Neutral), fill = Question.Type)) +
  geom_boxplot(position = position_dodge(width = 0.9)) +
  ggtitle(bquote("Question Type")) +
  my_theme1 +
  labs(title = " Log Neutral - Qlevel", x = "", y = "") +
  stat_summary(
    fun.data = n_fun, geom = "text", fun.y = median,
    parse = T, size = 5, vjust = -0.75, hjust = -0.75, angle = 90,
    position = position_dodge(width = 0.75)
  )

# Valence.Qtype.LogNeutral


# Valence.Qtype.Others <- Valence.Qlevel %>%
#   ggplot(aes(x = Question.Type, y = Others, fill = Question.Type)) +
#   geom_boxplot(position = position_dodge(width = 0.9)) +
#   ggtitle(bquote("Question Type")) +
#   my_theme1 +
#   labs(title = "Others - Qlevel", x = "", y = "") +
#   stat_summary(
#     fun.data = n_fun, geom = "text", fun.y = median,
#     parse = T, size = 5, vjust = -0.75, hjust = -0.75, angle = 90,
#     position = position_dodge(width = 0.75)
#   )

# Valence.Qtype.Others


Valence.Qtype.Afraid <- Valence.Qlevel %>%
  ggplot(aes(x = Question.Type, y = Afraid, fill = Question.Type)) +
  geom_boxplot(position = position_dodge(width = 0.9)) +
  ggtitle(bquote("Question Type")) +
  my_theme1 +
  labs(title = "Afraid - Qlevel", x = "", y = "") +
  stat_summary(
    fun.data = n_fun, geom = "text", fun.y = median,
    parse = T, size = 5, vjust = -0.75, hjust = -0.75, angle = 90,
    position = position_dodge(width = 0.75)
  )

ggarrange(Valence.Qtype.boxplot, Valence.Qtype.LogHappy,
  Valence.Qtype.Neutral, Valence.Qtype.Afraid,
  Valence.Qtype.Sad,
  #Valence.Qtype.Others,
  ncol = 2, nrow = 3
)
```

```{r echo=FALSE, fig.height=7, fig.width=7, message=FALSE, warning=FALSE}
require(MASS)
library("car")
par(mfrow = c(2, 2))
p1 <- with(Valence.Qlevel, qqp(Happy, "norm", main = "Happy"))
p1 <- with(Valence.Qlevel, qqp(log(Happy), "norm", main = "Log Happy"))
p1 <- with(Valence.Qlevel, qqp(Afraid, "norm", main = "Afraid"))
p1 <- with(Valence.Qlevel, qqp(log(Afraid), "norm", main = "Log Afraid"))
```

# Model 6 - Valence

## Happy Full Model

```{r echo=FALSE}

M6.Valence.fit.fm <- lmer(log(Happy) ~ (1 | ParticipantID) + Question.Type, data = Valence.Qlevel)

summary(M6.Valence.fit.fm)
summ(M6.Valence.fit.fm, digits = 3)
```

### Plot Final Happy Model Predictors

```{r fig.height=3, fig.width=6}
# Question Type Final Model
Valence_h.qt.pm.fm <- ggpredict(M6.Valence.fit.fm,
  terms = c("Question.Type")
) %>%
  mutate(group = as.factor(c("1", "2", "3"))) %>%
  drop_na() %>%
  gather(key = "key", value = "value", conf.low, conf.high) %>%
  ggplot() +
  geom_line(aes(x = x, y = value, color = group), size = 2) +
  geom_point(aes(x = x, y = predicted, color = group, size = 2)) +
  theme_bw() +
  scale_color_manual(values = c("gray", "black", "orange")) +
  scale_y_continuous(
    limits = c(0.004, 0.018),
    breaks = seq(0, 1, by = 0.005) # Sets y-axis breaks to increase by 0.1
  ) +
  my_theme_pred +
  labs(x = "", y = 
       #  expression(bold(ln) * bold(paste(bolditalic(P(H)) * ""))),
       #TeX(r'($\textit{ln}(P(HAPPY))$)'),
       TeX("$\\bar{\\textit{ln(HAPPY)}}"),
        title = TeX("$QTYPE$")
       )


Valence_h.qt.pm.fm
```

### Fixed Effects Visualization of Happy Model

```{r fig.height=4.5, fig.width=7}

pp.fm.plot.pred <- sjPlot::plot_model(M6.Valence.fit.fm,
  show.values = TRUE, show.p = TRUE,
  axis.labels = c("QC[W]", "QC[A]"),
  value.offset = 0.1,
  title = "Happy Final Model "
) + my_theme1 #+ xlim(-0.2, 0.2)

pp.fm.plot.pred$layers[[3]]$aes_params$vjust <- (0.1)
pp.fm.plot.pred$layers[[3]]$aes_params$hjust <- (0.3)

# pp.fm.plot.pred$data$term <- c("Question.TypeA", "Question.TypeW", "Grade")

pp.fm.plot.pred

# random effects
# plot_model(M4.fit.FM, "re")
```

### Diagnostic on Happy Model residuals

```{r echo=FALSE}
# Diagnostic on Model residuals

M6.Valence.fit.fm.res <- residuals(M6.Valence.fit.fm, type = "pearson")

qqnorm(M6.Valence.fit.fm.res, main = "Normal Q-Q Plot | Happy Model residuals")
qqline(M6.Valence.fit.fm.res, col = "red")
```


## Afraid Full Model

```{r echo=FALSE}
M6.af.fit.fm <- lmer(Afraid ~ (1 | ParticipantID) + Question.Type, data = Valence.Qlevel)

summary(M6.af.fit.fm)
summ(M6.af.fit.fm, digits = 3)
```

### Plot Final Afraid Model Predictors

```{r fig.height=3, fig.width=6}
# Question Type Final Model
Valence_af.qt.pm.fm <- ggpredict(M6.af.fit.fm,
  terms = c("Question.Type")
) %>%
  mutate(group = as.factor(c("1", "2", "3"))) %>%
  drop_na() %>%
  gather(key = "key", value = "value", conf.low, conf.high) %>%
  ggplot() +
  geom_line(aes(x = x, y = value, color = group), size = 2) +
  geom_point(aes(x = x, y = predicted, color = group, size = 2)) +
  theme_bw() +
  scale_color_manual(values = c("gray", "red", "black")) +
#  scale_y_continuous(labels = scales::percent) +
  scale_y_continuous(
    limits = c(0.1, 0.3),
    breaks = seq(0, 1, by = 0.1) # Sets y-axis breaks to increase by 0.1
  ) +
  my_theme_pred +
  labs(x = "", y = TeX("$\\bar{\\textit{AFRAID}}"),
      title = TeX("$QTYPE$")
       )


Valence_af.qt.pm.fm
```

### Fixed Effects Visualization of Afraid Model

```{r fig.height=4.5, fig.width=7}
af.fm.plot.pred <- sjPlot::plot_model(M6.af.fit.fm,
  show.values = TRUE, show.p = TRUE,
  axis.labels = c("QC[W]", "QC[A]"),
  value.offset = 0.1,
  title = "Afraid Final Model "
) + my_theme1

af.fm.plot.pred$layers[[3]]$aes_params$vjust <- (0.1)
af.fm.plot.pred$layers[[3]]$aes_params$hjust <- (0.3)


af.fm.plot.pred
```

### Diagnostic on Afraid Model residuals

```{r echo=FALSE}
# Diagnostic on Model residuals

M6.af.fit.fm.res <- residuals(M6.af.fit.fm, type = "pearson")

qqnorm(M6.af.fit.fm.res, main = "Normal Q-Q Plot | Afraid Model residuals")
qqline(M6.af.fit.fm.res, col = "red")
```


\newpage

# Paper figures - Figure13

# Valence and Performance

```{r fig.height=6, fig.width=11}

valence_final = cowplot::plot_grid(
Valence_h.qt.pm.fm,
Valence_af.qt.pm.fm, NULL,
  nrow = 1,
  scale = c(.97, .97, .97),
  labels = c("a1", "a2", "" ),
  label_size = 20
)





Grade_final <- cowplot::plot_grid(gradePP.qt.pm,
  gradePP_sai.pm, gradePP_pp.fm,
  nrow = 1,
  scale = c(.97, .97, .97),
  labels = c("b1", "b2", "b3" ),
  label_size = 20
)



final <- cowplot::plot_grid(
  valence_final, Grade_final, mylegend,
  nrow = 3,
  #scale = c(.97, .97, 0.01),
  rel_heights = c(1, 1, 0.1),
  label_size = 20
)

final
if (is_save == TRUE) {
  ggsave(
  filename = sprintf("%sFigure13.pdf", plot_dir), #Valence-Grade-Plots.pdf
  plot = final,
  width = 11,
  height = 6,
  dpi = 300
  )
}
```





# Valence Table III

```{r Valence-table3, echo=FALSE}

# 1) Put your models in a named list

models_valence <- list(
  Happy = M6.Valence.fit.fm,
  Afraid = M6.af.fit.fm
)

#mod= models_valence[["Happy"]]
# 2) extract each summary(...$coefficients) into a data.frame
coef_dfs_valence <- lapply(models_valence, function(mod) {
  co <- summ(mod, digits = 3)$coeftable
  #as.data.frame(co, stringsAsFactors = FALSE)
  as.data.frame(co, stringsAsFactors = FALSE) %>% dplyr::select(-4)
})

# assume coef_dfs is your list of 4 data.frames,
# each with rownames = predictor names and columns Est., S.E., t val., d.f., p
# 1) figure out every predictor that appears in any model
all_preds_valence <- unique(unlist(lapply(coef_dfs_valence, rownames)))
# 2) for each df, turn rownames into a column,
#    re-order to 'all_preds', and then put rownames back
aligned_valence <- lapply(coef_dfs_valence, function(df) {
  df2 <- as.data.frame(df, stringsAsFactors=FALSE)
  df2$Predictor <- rownames(df2)

  # reorder (and insert NA rows for missing preds)
  df2 <- df2[match(all_preds_valence, df2$Predictor), , drop=FALSE]

  # restore rownames
  rownames(df2) <- all_preds_valence
  df2
})

# 3) drop the extra Predictor columns except in the first
for(i in seq_along(aligned_valence)) {
  aligned_valence[[i]]$Predictor <- NULL
}

# 4) now cbind them
merged_valence <- do.call(cbind, aligned_valence)

# 5) restore a single Predictor column in front
merged_valence <- cbind(Predictor = rownames(merged_valence), merged_valence, row.names=NULL)

# inspect
#print(merged_valence)


# Select all columns that end with ".Est." and drop them
Est_all <- merged_valence %>% dplyr::select(Predictor,ends_with(".Est."))
SE_all <- merged_valence %>% dplyr::select(Predictor,ends_with(".S.E."))
t_all <- merged_valence %>% dplyr::select(Predictor,ends_with(".t val."))
p_all <- merged_valence %>% dplyr::select(Predictor,ends_with(".p"))

paper_merged <- cbind(Est_all, SE_all[, -1], t_all[, -1], p_all[, -1])




```


```{r valence-merged-table, results='asis', echo=FALSE}
# 2) Build your header labels
stat_labels  <- c("Est", "S.E.", "t", "p")
#stat_labels  <- c("$Est.$", "$S.E.$", "$z$ value", "Pr($>|z|$)")
# bottom row: model names repeated under each stat
model_names  <- c("HAPPY", "FEAR")
var_labels   <- rep(model_names, times = length(stat_labels))

# define a very light and a medium light gray
light_gray  <- if (knitr::is_latex_output()) "gray!25" else "#E6E6E6"
medium_gray <- if (knitr::is_latex_output()) "gray!50" else "#CCCCCC"


paper_merged %>%    
  mutate(
    across(
      ends_with(".p"),
      ~ round(., 3)
    )
  ) %>%
  mutate(
    across(
      ends_with(".p"),
      ~ format.pval(., digits = 2, eps = 0.001)
    )
  ) %>% 
  kable(
  digits = 3,
  format          = "html",
  #format          = "latex",
  booktabs        = TRUE,
  escape          = TRUE,
  table.placement = "H",
  col.names       = c("Predictor", var_labels),
  align           = c("l", rep("r", length(var_labels)))
) %>%
  add_header_above(
    header = c(
      " "    = 1,
      "Coefficient $b.$"    = 2,
      "$S.E.$" = 2,
      "$t$ value" = 2,
      "Pr(>$|z|$)"  = 2
    ),
    bold = TRUE
  ) %>%
  column_spec(c(3,5, 7,9),   background = light_gray) %>% # myGray (0.8), #"gray!15"
  #column_spec(c(5, 9, 13 ,17),   background = medium_gray) %>%  # gray 0.7
  #column_spec(c(4,6,8),   background = "white")    %>%
  kable_styling(
    latex_options = c("hold_position","scale_down"),
    #bootstrap_options = c("striped", "hover", "condensed"),
    font_size     = 11
  )
```






# Performance Table IV

```{r echo=FALSE}
# 1) Put your models in a named list

models_valence <- list(
  Grade = M5.fit.fm
)

#mod= models_valence[["Happy"]]
# 2) extract each summary(...$coefficients) into a data.frame
coef_dfs_valence <- lapply(models_valence, function(mod) {
  co <- summ(mod, digits = 3)$coeftable
  as.data.frame(co, stringsAsFactors = FALSE)
    
})

# assume coef_dfs is your list of 4 data.frames,
# each with rownames = predictor names and columns Est., S.E., t val., d.f., p
# 1) figure out every predictor that appears in any model
all_preds_valence <- unique(unlist(lapply(coef_dfs_valence, rownames)))
# 2) for each df, turn rownames into a column,
#    re-order to 'all_preds', and then put rownames back
aligned_valence <- lapply(coef_dfs_valence, function(df) {
  df2 <- as.data.frame(df, stringsAsFactors=FALSE)
  df2$Predictor <- rownames(df2)

  # reorder (and insert NA rows for missing preds)
  df2 <- df2[match(all_preds_valence, df2$Predictor), drop=FALSE]

  # restore rownames
  rownames(df2) <- all_preds_valence
  df2
})

# 3) drop the extra Predictor columns except in the first
for(i in seq_along(aligned_valence)) {
  aligned_valence[[i]]$Predictor <- NULL
}

# 4) now cbind them
merged_valence <- do.call(cbind, aligned_valence)

# 5) restore a single Predictor column in front
merged_valence <- cbind(Predictor = rownames(merged_valence), merged_valence, row.names=NULL)

# inspect
#print(merged_valence)


paper_merged <- 
# merge all on Predictor column
merged_valence %>%
  dplyr::select(Predictor, ends_with(".Est.")) %>%
  dplyr::rename(Est = ends_with(".Est.")) %>%
  dplyr::left_join(
    merged_valence %>% dplyr::select(Predictor, ends_with(".S.E.")) %>% dplyr::rename(SE = ends_with(".S.E.")),
    by = "Predictor"
  ) %>%
  dplyr::left_join(
    merged_valence %>% dplyr::select(Predictor, ends_with(".z val.")) %>% dplyr::rename(z = ends_with(".z val.")),
    by = "Predictor"
  ) %>%
  dplyr::left_join(
    merged_valence %>% dplyr::select(Predictor, ends_with(".p")) %>% dplyr::rename(p = ends_with(".p")),
    by = "Predictor"
  )


```


```{r grade-merged-table, results='asis', echo=FALSE}
# 2) Build your header labels
stat_labels  <- c("Coefficient $b.$", "$S.E.$", "$z$ value", "Pr(>$|z|$)")
# bottom row: model names repeated under each stat
model_names  <- c("Grade")
var_labels   <- rep(model_names, times = length(stat_labels))

paper_merged %>% 
    mutate(
     p = format.pval(p, digits = 2, eps = 0.001)
  ) %>%
  kable(
  digits = 3,
  format          = "html",
  #format          = "latex",
  booktabs        = TRUE,
  escape          = TRUE,
  table.placement = "H",
  col.names       = c("Predictor", stat_labels),
  align           = c("l", rep("r", length(stat_labels)))
) %>%
  kable_styling(
    latex_options = c("hold_position","scale_down"),
    bootstrap_options = c("striped", "hover", "condensed"),
    font_size     = 11
  )
```





